### 2023-01-15 index.qmd
init

---
title: "Lawrence Bull, PhD"
about:
  template: solana
  image: images/mugshot.png
  links:
    - text: github
      href: https://github.com/labull
    - text: google scholar
      href: https://scholar.google.com/citations?user=Lszt1B4AAAAJ&hl=en
    - text: research gate
      href: https://www.researchgate.net/profile/Lawrence-Bull-2
    - text: orcid
      href: https://orcid.org/0000-0002-0225-5010
    - text: twitter
      href: https://twitter.com/lwrncebull?lang=ar
---

<div style="text-align: left">

**[2022-2027] University of Cambridge** | [Computational Statistics and Machine Learning Group](https://csml-cam.github.io) | Research Associate | Department of Engineering

**[2021-2022] The Alan Turing Institute** | Research Associate | [Data-Centric Engineering](https://www.turing.ac.uk/research/research-programmes/data-centric-engineering)

**[2016-2021] University of Sheffield** | PhD Student (2016-2019) Research Assistant (2019-2022) | [Dynamics Research Group](https://drg.ac.uk/) | Department of Engineering

</br>

Broadly speaking, I'm a researcher in statistical methods for Data-Centric Engineering. Focussing on monitoring techniques for telemetry data from systems and infrastructure.

I'm particularly interested in _multilevel structures_ that appear in measurements from interconnected populations of systems -- trains, [planes](), [automobiles](https://doi.org/10.48550/arXiv.2204.12404) (... [wind turbines](https://arxiv.org/abs/2111.15496)).
By encoding domain expertise in a Bayesian workflow, complex models can be built from interpretable units, allowing machines to share information and increase the value of data.
At the population level, alternative insights can emerge that might otherwise be missed -- the whole is something _besides_ its parts.

I'm a communications editor for the [Data-Centric Engineering](https://www.cambridge.org/core/journals/data-centric-engineering) journal (Cambridge University Press) and a member of the [Early-Career Academic and Professionals Panel](https://www-smartinfrastructure.eng.cam.ac.uk/news/csic-call-applicants-early-career-academics-and-professionals-panel) (ECAPP) in the [Cambridge Centre for Smart Infrastructure and Construction](https://www-smartinfrastructure.eng.cam.ac.uk/) (CSIC).

### 2023-01-15 papers.qmd
init

---
title: "Papers"
---

|    | Journal papers                                                                                                                                                                                                                                                                            |
|---:|:------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------|
|  3 | **Bull**, Dhada, Steinert, Lindgren, Parlikad, Duncan, Girolami [Knowledge Transfer in Engineering Fleets: Hierarchical Bayesian Modelling for Multi-Task Learning](https://arxiv.org/abs/2204.12404) (2022)                                                                              |
|  4 | **Bull**, Dervilis, Worden, Cross, Rogers [A sampling-based approach for information-theoretic inspection management](https://royalsocietypublishing.org/doi/abs/10.1098/rspa.2021.0790) (2022)                                                                                           |
|  8 | Gardner, **Bull**, Gosliga, Poole, Dervilis, Worden [A population-based SHM methodology for heterogeneous structures: Transferring damage localisation knowledge between different aircraft wings](https://www.sciencedirect.com/science/article/pii/S0888327022001030) (2022)            |
| 10 | **Bull**, Gardner, Rogers, Dervilis, Cross, Papatheou, Maguire, Campos, Worden [Bayesian modelling of multivalued power curves from an operational wind farm](https://www.sciencedirect.com/science/article/pii/S0888327021008724) (2022)                                                 |
| 11 | Gardner, **Bull**, Dervilis, Worden [Domain-adapted Gaussian mixture models for population-based structural health monitoring](https://link.springer.com/article/10.1007/s13349-022-00565-5) (2022)                                                                                       |
| 13 | Gardner, **Bull**, Dervilis, Worden [On the application of kernelised Bayesian transfer learning to population-based structural health monitoring](https://www.sciencedirect.com/science/article/pii/S088832702100861X) (2022)                                                            |
| 14 | Hughes, **Bull**, Gardner, Barthorpe, Dervilis, Worden [On risk-based active learning for structural health monitoring](https://www.sciencedirect.com/science/article/pii/S0888327021009055) (2022)                                                                                       |
| 18 | Dardeno, Haywood-Alexander, Mills, **Bull**, Dervilis, Worden [Investigating the effects of ambient temperature on feature consistency in vibration-based SHM](https://scholar.google.com/scholar?cluster=624769372939145628&hl=en&oi=scholarr) (2022)                                    |
| 19 | Dardeno, **Bull**, Dervilis, Worden [Investigating experimental repeatability and feature consistency in vibration-based SHM](https://scholar.google.com/scholar?cluster=10140930682997029543&hl=en&oi=scholarr) (2022)                                                                   |
| 25 | Gardner, **Bull**, Dervilis, Worden [Overcoming the problem of repair in structural health monitoring: Metric-informed transfer learning](https://www.sciencedirect.com/science/article/pii/S0022460X21003175) (2021)                                                                     |
| 27 | **Bull**, Gardner, Dervilis, Papatheou, Haywood-Alexander, Mills, Worden [On the transfer of damage detectors between structures: an experimental case study](https://www.sciencedirect.com/science/article/pii/S0022460X21001449) (2021)                                                 |
| 28 | **Bull**, Gardner, Rogers, Cross, Dervilis, Worden [Probabilistic inference for structural health monitoring: new modes of learning from data](https://ascelibrary.org/doi/abs/10.1061/AJRUA6.0001106) (2021)                                                                             |
| 29 | Gardner, **Bull**, Gosliga, Dervilis, Worden [Foundations of population-based SHM, Part III: Heterogeneous populations–Mapping and transfer](https://www.sciencedirect.com/science/article/pii/S0888327020305288) (2021)                                                                  |
| 30 | **Bull**, Gardner, Gosliga, Rogers, Dervilis, Cross, Papatheou, Maguire, Campos, Worden [Foundations of population-based SHM, Part I: Homogeneous populations and forms](https://www.sciencedirect.com/science/article/pii/S0888327020305276) (2021)                                      |
| 31 | Gosliga, Gardner, **Bull**, Dervilis, Worden [Foundations of Population-based SHM, Part II: Heterogeneous populations–Graphs, networks, and communities](https://www.sciencedirect.com/science/article/pii/S0888327020305306) (2021)                                                      |
| 32 | Poole, Gardner, Dervilis, **Bull**, Worden [On normalisation for domain adaptation in population-based structural health monitoring](https://scholar.google.com/scholar?cluster=9278611934387106844&hl=en&oi=scholarr) (2021)                                                             |
| 37 | Zammit, **Bull**, Sanders, Galvin, Dervilis, Sidhu, Worden [Towards the Probabilistic Analysis of Small Bowel Capsule Endoscopy Features to Predict Severity of Duodenal Histology in Patients with Villous Atrophy](https://link.springer.com/article/10.1007/s10916-020-01657-9) (2020) |
| 38 | Worden, **Bull**, Gardner, Gosliga, Rogers, Cross, Papatheou, Lin, Dervilis [A brief introduction to recent developments in population-based structural health monitoring](https://www.frontiersin.org/articles/10.3389/fbuil.2020.00146/full) (2020)                                     |
| 40 | **Bull**, Worden, Dervilis [Towards semi-supervised and probabilistic classification in structural health monitoring](https://www.sciencedirect.com/science/article/pii/S088832702030039X) (2020)                                                                                         |
| 46 | **Bull**, Rogers, Wickramarachchi, Cross, Worden, Dervilis [Probabilistic active learning: an online framework for structural health monitoring](https://www.sciencedirect.com/science/article/pii/S0888327019305096) (2019)                                                              |
| 47 | **Bull**, Worden, Fuentes, Manson, Cross, Dervilis [Outlier ensembles: A robust method for damage detection and unsupervised feature extraction from high-dimensional data](https://www.sciencedirect.com/science/article/pii/S0022460X1930197X) (2019)                                   |
| 55 | **Bull**, Worden, Manson, Dervilis [Active learning for semi-supervised structural health monitoring](https://www.sciencedirect.com/science/article/pii/S0022460X18305479) (2018)                                                                                                         |

|    | Preprints                                                                                                                                                                                       |
|---:|:------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------|
|  5 | Hughes, **Bull**, Gardner, Dervilis, Worden [Mitigating sampling bias in risk-based active learning via an EM algorithm](https://arxiv.org/abs/2206.12598) (2022)                               |
|  6 | Dardeno, **Bull**, Dervilis, Worden [A generalised form for a homogeneous population of structures using an overlapping mixture of Gaussian processes](https://arxiv.org/abs/2206.11683) (2022) |
|  7 | Hughes, Gardner, **Bull**, Dervilis, Worden [Improving decision-making via risk-based active learning: Probabilistic discriminative classifiers](https://arxiv.org/abs/2206.11616) (2022)       |
|  9 | Poole, Gardner, Dervilis, **Bull**, Worden [On statistic alignment for domain adaptation in structural health monitoring](https://arxiv.org/abs/2205.12052) (2022)                              |
| 15 | Dardeno, **Bull**, Mills, Dervilis, Worden [Modelling variability in vibration-based PBSHM via a generalised population form](https://arxiv.org/abs/2203.07115) (2022)                          |
| 16 | Hughes, **Bull**, Gardner, Dervilis, Worden [On robust risk-based active-learning algorithms for enhanced decision support](https://arxiv.org/abs/2201.02555) (2022)                            |

|    | Book chapters                                                                                                                                                                                                                 |
|---:|:------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------|
| 20 | **Bull**, Hughes, Rogers, Gardner, Worden, Dervilis [Partially Supervised Learning for Data-Driven Structural Health Monitoring](https://link.springer.com/chapter/10.1007/978-3-030-81716-9_19) (2022)                       |
| 21 | Gardner, **Bull**, Gosliga, Dervilis, Cross, Papatheou, Worden [Population-Based Structural Health Monitoring](https://link.springer.com/chapter/10.1007/978-3-030-81716-9_20) (2022)                                         |
| 41 | Fuentes, Cross, Gardner, **Bull**, Rogers, Barthorpe, Shi, Dervilis, Farrar, Worden [Structural Health Monitoring and Damage Identification](https://link.springer.com/content/pdf/10.1007/978-1-4939-6503-8_23-1.pdf) (2020) |

|    | Thesis                                                                                                                                |
|---:|:--------------------------------------------------------------------------------------------------------------------------------------|
| 51 | **Bull** [Towards probabilistic and partially-supervised structural health monitoring](https://etheses.whiterose.ac.uk/26282/) (2019) |

|    | Conference papers                                                                                                                                                                                                                                                                                                                                                          |
|---:|:---------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------|
|  1 | Poole, Gardner, Dervilis, **Bull**, Worden [On the Application of Partial Domain Adaptation for PBSHM](https://link.springer.com/chapter/10.1007/978-3-031-07322-9_42) (2023)                                                                                                                                                                                              |
|  2 | Dhada, **Bull**, Girolami, Parlikad [Modelling the Times-to-Failures Using a Statistical Hierarchical Model](https://link.springer.com/chapter/10.1007/978-3-031-07258-1_99) (2023)                                                                                                                                                                                        |
| 12 | **Bull**, Dhada, Steinert, Lindgren, Parlikad, Girolami [Population-Level Modelling for Truck Fleet Survival Analysis](https://aspace.repository.cam.ac.uk/handle/1810/335452) (2022)                                                                                                                                                                                      |
| 17 | Hughes, **Bull**, Gardner, Dervilis, Worden, Hughes [Semi-supervised risk-based active learning using inspection and maintenance information](https://eprints.whiterose.ac.uk/191598/) (2022)                                                                                                                                                                              |
| 22 | Gardner, **Bull**, Dervilis, Worden [Challenges for SHM from Structural Repairs: An Outlier-Informed Domain Adaptation Approach](https://link.springer.com/chapter/10.1007/978-3-030-76004-5_10) (2022)                                                                                                                                                                    |
| 23 | Gardner, **Bull**, Dervilis, Worden [On the Application of Heterogeneous Transfer Learning to Population-Based Structural Health Monitoring](https://link.springer.com/chapter/10.1007/978-3-030-76004-5_11) (2022)                                                                                                                                                        |
| 24 | **Bull**, Gardner, Dervilis, Papatheou, Haywood-Alexander, Mills, Worden [Transferring Damage Detectors Between Tailplane Experiments](https://link.springer.com/chapter/10.1007/978-3-030-76004-5_22) (2022)                                                                                                                                                              |
| 26 | Hughes, **Bull**, Gardner, Barthorpe, Dervilis, Worden [A risk-based active learning approach to inspection scheduling](https://www.researchgate.net/profile/Aidan-Hughes-4/publication/355903488_A_risk-based_active_learning_approach_to_inspection_scheduling/links/61892373d7d1af224bc69a96/A-risk-based-active-learning-approach-to-inspection-scheduling.pdf) (2021) |
| 33 | **Bull**, Gardner, Dervilis, Papatheou, Worden [Automated Feature Extraction for Damage Detection: A Pseudo-fault Framework for Population-based SHM]() (2021)                                                                                                                                                                                                             |
| 34 | **Bull**, Gardner, Dervilis, Worden [Normalising Flows and Nonlinear Normal Modes](https://www.sciencedirect.com/science/article/pii/S240589632101209X) (2021)                                                                                                                                                                                                             |
| 35 | Gosliga, Gardner, **Bull**, Dervilis, Worden [Towards population-based structural health monitoring, Part III: Graphs, networks and communities](https://link.springer.com/chapter/10.1007/978-3-030-47717-2_26) (2021)                                                                                                                                                    |
| 36 | Gosliga, Gardner, **Bull**, Dervilis, Worden [Towards population-based structural health monitoring, Part II: heterogeneous populations and structures as graphs](https://link.springer.com/chapter/10.1007/978-3-030-47717-2_17) (2021)                                                                                                                                   |
| 39 | **Bull**, Gardner, Rogers, Cross, Dervilis, Worden [New Modes of Inference for Probabilistic SHM](https://link.springer.com/chapter/10.1007/978-3-030-64908-1_39) (2020)                                                                                                                                                                                                   |
| 42 | Gardner, **Bull**, Gosliga, Dervilis, Worden [Towards population-based structural health monitoring, Part IV: heterogeneous populations, transfer and mapping](https://link.springer.com/chapter/10.1007/978-3-030-47638-0_20) (2020)                                                                                                                                      |
| 43 | Gardner, **Bull**, Dervilis, Worden [Kernelised Bayesian transfer learning for population-based structural health monitoring](https://link.springer.com/chapter/10.1007/978-3-030-47638-0_22) (2020)                                                                                                                                                                       |
| 44 | **Bull**, Gardner, Gosliga, Dervilis, Papatheou, Maguire, Campos, Rogers, Cross, Worden [Towards population-based structural health monitoring, Part I: Homogeneous populations and forms](https://link.springer.com/chapter/10.1007/978-3-030-47638-0_32) (2020)                                                                                                          |
| 45 | **Bull**, Worden, Rogers, Cross, Dervilis [Investigating engineering data by probabilistic measures](https://link.springer.com/chapter/10.1007/978-3-030-12243-0_12) (2020)                                                                                                                                                                                                |
| 48 | **Bull**, Worden, Rogers, Wickramarachchi, Cross, McLeay, Leahy, Dervilis [A probabilistic framework for online structural health monitoring: active learning from machining data streams](https://iopscience.iop.org/article/10.1088/1742-6596/1264/1/012028/meta) (2019)                                                                                                 |
| 49 | **Bull**, Rogers, Dervilis, Cross, Worden [A Gaussian process form for population-based structural health monitoring](https://eprints.whiterose.ac.uk/148168/) (2019)                                                                                                                                                                                                      |
| 50 | **Bull**, Dervilis, Worden [Experimental Validation of the Population-Form to Represent Nominally-Identical Systems](https://scholar.google.com/scholar?cluster=7507461710880003650&hl=en&oi=scholarr) (2019)                                                                                                                                                              |
| 52 | **Bull**, Worden, Dervilis [Damage classification using labelled and unlabelled measurements](https://www.researchgate.net/profile/Lawrence-Bull-2/publication/337303717_Damage_Classification_Using_Labelled_and_Unlabelled_Measurements/links/62276fc93c53d31ba4b15c45/Damage-Classification-Using-Labelled-and-Unlabelled-Measurements.pdf) (2019)                      |
| 53 | Dervilis, Zhang, **Bull**, Cross, Rogers, Fuentes, Dertimanis, Abdallah, Chatzi, Worden [A nonlinear robust outlier detection approach for SHM](https://eprints.whiterose.ac.uk/147321/) (2019)                                                                                                                                                                            |
| 54 | **Bull**, Manson, Worden, Dervilis [Active Learning Approaches to Structural Health Monitoring](https://link.springer.com/chapter/10.1007/978-3-319-75390-4_14) (2019)                                                                                                                                                                                                     |
| 56 | **Bull**, Worden, Cross, Dervilis [Outlier Ensembles: an Alternative Robust Method for Inclusive Outlier Analysis with Structural Health Monitoring Data]() (2018)                                                                                                                                                                                                         |

| Other   |
|---------|

### 2023-01-15 software.qmd
init

---
title: "Software"
---

# [`EPR`](https://github.com/labull/EngineeringPatternRecognition)

Code to reproduce paper results (or as close as possible, depending on 
data-availability). Each publication has a Jupyter notebook.

Mostly probabilistic/Bayesian ML for engineering applications, particularly 
performance and health monitoring. Scripts are provided to test and 
demonstrate the _EPR_ module.

## Notebooks for papers

* [Hierarchical Bayesian modelling for knowledge transfer across engineering fleets via multitask learning (CACAIE, 2022)](https://doi.org/10.1111/mice.12901)
  * Hierarchical regression models of engineering populations, allowing 
    knowledge transfer between subgroups.
  * Applications to truck fleet survival analysis and wind farm power 
    prediction.
  * Jupyter notebook [demo](https://github.com/labull/EngineeringPatternRecognition/tree/main/Knowledge-transfer-in-engineering-fleets.ipynb) 
    based on truck-fleet survival analysis.

* [On the transfer of damage detectors between structures: an experimental 
  case study (JSV, 2021)](https://doi.org/10.1016/j.jsv.2021.116072)
  * Domain adaptation to transfer novelty detectors between aircraft 
    tailplane ground-tests.
  * The [TCA code](https://github.com/labull/EngineeringPatternRecognition/tree/main/TCAdemo.py) used in the papers.

* [Towards semi-supervised and probabilistic classification in structural 
  health monitoring (MSSP, 2020)](https://doi.org/10.1016/j.ymssp.2020.106653)
  * Semi-supervised learning of GMMs via (MAP) expectation maximisation, 
    applied to Gnat aircraft ground-test data to utilise both labelled 
    and unlabelled data.
  * Jupyter notebook 
  [demo](https://github.com/labull/EngineeringPatternRecognition/tree/main/Semi-supervised-and-probabilistic-classification-in-SHM-MSSP2020.ipynb); 
  MATLAB [demo](https://github.com/labull/EngineeringPatternRecognition/tree/main/matlab/semi_supervised_GMM).

* [Probabilistic active learning: An online framework for structural health 
  monitoring (MSSP, 2019)](https://doi.org/10.1016/j.ymssp.2019.106294)
  * Uncertainty sampling (GMMs) to direct inspections from online data 
    streams from engineering systems. Applied to bridge, lathe, and
    aircraft monitoring datasets.
  * Jupyter notebook 
  [demo](https://github.com/labull/EngineeringPatternRecognition/tree/main/Probabilistic-active-learning-An-online-framework-for-SHM-MSSP2019.ipynb); 
  MATLAB [demo](https://github.com/labull/EngineeringPatternRecognition/tree/main/matlab/active_learning_GMM).

* [Active learning for semi-supervised structural health monitoring (JSV, 
  2018)](https://doi.org/10.1016/j.jsv.2018.08.040)
  * Hierarchical sampling for active learning (the DH active 
    learner) applied to learn a classifier for ground-test vibration data 
    from a Gnat aircraft.
  * MATLAB [demo](https://github.com/labull/EngineeringPatternRecognition/tree/main/matlab/cluster_based_active_learning).

## Algorithms

* Multitask Learning
    * [Hierarchical regression](https://www.taylorfrancis.com/books/mono/10.1201/9780429258411/bayesian-data-analysis-andrew-gelman-john-carlin-hal-stern-donald-rubin) (Stan)

* Domain Adaptation
  * [Transfer Component Analysis](https://ieeexplore.ieee.org/stamp/stamp.jsp?arnumber=5640675&casa_token=Go7wJy20s-QAAAAA:-LZaw0y0LDV7TFK4ClCSoDbsPWF87A-GD2iklRy3ObjxL7A0lanOe92vM-UCd_WwJY7th6R3-SE) (TCA)

* Partially-supervised learning
  * [Active learning by uncertainty sampling in Gaussian Mixture Models](https://doi.org/10.1016/j.ymssp.2019.106294) 
    (GMMs)
  * [Semi-supervised learning of mixture models](https://www.morganclaypool.com/doi/pdfplus/10.2200/S00196ED1V01Y200906AIM006?casa_token=0YqCaqxyR1EAAAAA:v8kqB5LBhkclcS30fp0z9DOELXhwlPrqZV2YjJiAK2CuGAPNVoDgId_bODlX6mifibxb1ozTbio) 
  via (MAP) expectation 
    maximisation
  * [Hierarchical sampling for active learning](https://dl.acm.org/doi/pdf/10.1145/1390156.1390183?casa_token=MaX0vwAsl9kAAAAA:ADzBT6YbRvKUh6DfZOGB1O-eqO8q7v1JLTBLgcN263vjoROp4D6wc3MHkcwxMzX20cgPimPI-Ibx6g)
   (the DH active learner)

[Github repo](https://github.com/labull/EngineeringPatternRecognition)

### 2023-01-15 writing.qmd
init

# Writing

Tutorial and course notes -- shared for reading group and teaching purposes.
Also blog posts to support and explain research papers.

## Notes
### [Probability primer]()
Notes for the ROSEHIPS reading group (TBC).

### [Introduction to Engineering Pattern Recognition](https://github.com/labull/EPR-lectures)
Guest Lectures for the Advanced Dynamics course at the University of Sheffield in the Engineering dept.
A light introduction to machine learning in the context of some engineering examples:

- EPR1 | Classifying acoustic emission signals

- EPR2 | Regression analysis of wind turbine power curves

## Paper summaries

### 2023-01-16 index.qmd
edit index

@@
 
-I'm particularly interested in _multilevel structures_ that appear in measurements from interconnected populations of systems -- trains, [planes](), [automobiles](https://doi.org/10.48550/arXiv.2204.12404) (...
+I'm particularly interested in _multilevel structures_ that appear in measurements from populations of systems -- trains, [planes](), [automobiles](https://doi.org/10.48550/arXiv.2204.12404) (...
 [wind turbines](https://arxiv.org/abs/2111.15496)).

### 2023-01-16 index.qmd
edit index, writing

@@
 [wind turbines](https://arxiv.org/abs/2111.15496)).
-By encoding domain expertise in a Bayesian workflow, complex models can be built from interpretable units, allowing machines to share information and increase the value of data.
+By encoding domain expertise in a Bayesian workflow, complex models can be built from interpretable units, allowing machines to share information and increasing the value of data.
 At the population level, alternative insights can emerge that might otherwise be missed -- the whole is something _besides_ its parts.

### 2023-01-16 writing.qmd
edit index, writing

@@
 ### [Introduction to Engineering Pattern Recognition](https://github.com/labull/EPR-lectures)
-Guest Lectures for the Advanced Dynamics course at the University of Sheffield in the Engineering dept.
+Guest Lectures for the Advanced Dynamics [MEC452] undergraduate course at the University of Sheffield in the Engineering Dept.
 A light introduction to machine learning in the context of some engineering examples:

### 2023-02-22 index.qmd
update links in index

@@
   image: images/mugshot.png
-  links:
-    - text: github
-      href: https://github.com/labull
-    - text: google scholar
-      href: https://scholar.google.com/citations?user=Lszt1B4AAAAJ&hl=en
-    - text: research gate
-      href: https://www.researchgate.net/profile/Lawrence-Bull-2
-    - text: orcid
-      href: https://orcid.org/0000-0002-0225-5010
-    - text: twitter
-      href: https://twitter.com/lwrncebull?lang=ar
 ---
+
+</br>
 
@@
 
-I'm particularly interested in _multilevel structures_ that appear in measurements from populations of systems -- trains, [planes](), [automobiles](https://doi.org/10.48550/arXiv.2204.12404) (...
+I'm particularly interested in _multilevel structures_ that appear in measurements from populations of systems -- trains, [planes](https://www.sciencedirect.com/science/article/pii/S0022460X21001449), [automobiles](https://doi.org/10.48550/arXiv.2204.12404) (...
 [wind turbines](https://arxiv.org/abs/2111.15496)).
@@
 I'm a communications editor for the [Data-Centric Engineering](https://www.cambridge.org/core/journals/data-centric-engineering) journal (Cambridge University Press) and a member of the [Early-Career Academic and Professionals Panel](https://www-smartinfrastructure.eng.cam.ac.uk/news/csic-call-applicants-early-career-academics-and-professionals-panel) (ECAPP) in the [Cambridge Centre for Smart Infrastructure and Construction](https://www-smartinfrastructure.eng.cam.ac.uk/) (CSIC).
+
+<div style="text-align: right">
+
+</br>
+
+[github](https://github.com/labull)
+
+[google scholar](https://scholar.google.com/citations?user=Lszt1B4AAAAJ&hl=en)
+
+[research gate](https://www.researchgate.net/profile/Lawrence-Bull-2)
+
+[orcid](https://orcid.org/0000-0002-0225-5010)
+
+[twitter](https://twitter.com/lwrncebull?lang=ar)

### 2023-05-26 papers.qmd
update the paper list

@@
 |---:|:------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------|
-|  3 | **Bull**, Dhada, Steinert, Lindgren, Parlikad, Duncan, Girolami [Knowledge Transfer in Engineering Fleets: Hierarchical Bayesian Modelling for Multi-Task Learning](https://arxiv.org/abs/2204.12404) (2022)                                                                              |
-|  4 | **Bull**, Dervilis, Worden, Cross, Rogers [A sampling-based approach for information-theoretic inspection management](https://royalsocietypublishing.org/doi/abs/10.1098/rspa.2021.0790) (2022)                                                                                           |
-|  8 | Gardner, **Bull**, Gosliga, Poole, Dervilis, Worden [A population-based SHM methodology for heterogeneous structures: Transferring damage localisation knowledge between different aircraft wings](https://www.sciencedirect.com/science/article/pii/S0888327022001030) (2022)            |
-| 10 | **Bull**, Gardner, Rogers, Dervilis, Cross, Papatheou, Maguire, Campos, Worden [Bayesian modelling of multivalued power curves from an operational wind farm](https://www.sciencedirect.com/science/article/pii/S0888327021008724) (2022)                                                 |
-| 11 | Gardner, **Bull**, Dervilis, Worden [Domain-adapted Gaussian mixture models for population-based structural health monitoring](https://link.springer.com/article/10.1007/s13349-022-00565-5) (2022)                                                                                       |
-| 13 | Gardner, **Bull**, Dervilis, Worden [On the application of kernelised Bayesian transfer learning to population-based structural health monitoring](https://www.sciencedirect.com/science/article/pii/S088832702100861X) (2022)                                                            |
-| 14 | Hughes, **Bull**, Gardner, Barthorpe, Dervilis, Worden [On risk-based active learning for structural health monitoring](https://www.sciencedirect.com/science/article/pii/S0888327021009055) (2022)                                                                                       |
-| 18 | Dardeno, Haywood-Alexander, Mills, **Bull**, Dervilis, Worden [Investigating the effects of ambient temperature on feature consistency in vibration-based SHM](https://scholar.google.com/scholar?cluster=624769372939145628&hl=en&oi=scholarr) (2022)                                    |
-| 19 | Dardeno, **Bull**, Dervilis, Worden [Investigating experimental repeatability and feature consistency in vibration-based SHM](https://scholar.google.com/scholar?cluster=10140930682997029543&hl=en&oi=scholarr) (2022)                                                                   |
-| 25 | Gardner, **Bull**, Dervilis, Worden [Overcoming the problem of repair in structural health monitoring: Metric-informed transfer learning](https://www.sciencedirect.com/science/article/pii/S0022460X21003175) (2021)                                                                     |
-| 27 | **Bull**, Gardner, Dervilis, Papatheou, Haywood-Alexander, Mills, Worden [On the transfer of damage detectors between structures: an experimental case study](https://www.sciencedirect.com/science/article/pii/S0022460X21001449) (2021)                                                 |
-| 28 | **Bull**, Gardner, Rogers, Cross, Dervilis, Worden [Probabilistic inference for structural health monitoring: new modes of learning from data](https://ascelibrary.org/doi/abs/10.1061/AJRUA6.0001106) (2021)                                                                             |
-| 29 | Gardner, **Bull**, Gosliga, Dervilis, Worden [Foundations of population-based SHM, Part III: Heterogeneous populations–Mapping and transfer](https://www.sciencedirect.com/science/article/pii/S0888327020305288) (2021)                                                                  |
-| 30 | **Bull**, Gardner, Gosliga, Rogers, Dervilis, Cross, Papatheou, Maguire, Campos, Worden [Foundations of population-based SHM, Part I: Homogeneous populations and forms](https://www.sciencedirect.com/science/article/pii/S0888327020305276) (2021)                                      |
-| 31 | Gosliga, Gardner, **Bull**, Dervilis, Worden [Foundations of Population-based SHM, Part II: Heterogeneous populations–Graphs, networks, and communities](https://www.sciencedirect.com/science/article/pii/S0888327020305306) (2021)                                                      |
-| 32 | Poole, Gardner, Dervilis, **Bull**, Worden [On normalisation for domain adaptation in population-based structural health monitoring](https://scholar.google.com/scholar?cluster=9278611934387106844&hl=en&oi=scholarr) (2021)                                                             |
-| 37 | Zammit, **Bull**, Sanders, Galvin, Dervilis, Sidhu, Worden [Towards the Probabilistic Analysis of Small Bowel Capsule Endoscopy Features to Predict Severity of Duodenal Histology in Patients with Villous Atrophy](https://link.springer.com/article/10.1007/s10916-020-01657-9) (2020) |
-| 38 | Worden, **Bull**, Gardner, Gosliga, Rogers, Cross, Papatheou, Lin, Dervilis [A brief introduction to recent developments in population-based structural health monitoring](https://www.frontiersin.org/articles/10.3389/fbuil.2020.00146/full) (2020)                                     |
-| 40 | **Bull**, Worden, Dervilis [Towards semi-supervised and probabilistic classification in structural health monitoring](https://www.sciencedirect.com/science/article/pii/S088832702030039X) (2020)                                                                                         |
-| 46 | **Bull**, Rogers, Wickramarachchi, Cross, Worden, Dervilis [Probabilistic active learning: an online framework for structural health monitoring](https://www.sciencedirect.com/science/article/pii/S0888327019305096) (2019)                                                              |
-| 47 | **Bull**, Worden, Fuentes, Manson, Cross, Dervilis [Outlier ensembles: A robust method for damage detection and unsupervised feature extraction from high-dimensional data](https://www.sciencedirect.com/science/article/pii/S0022460X1930197X) (2019)                                   |
-| 55 | **Bull**, Worden, Manson, Dervilis [Active learning for semi-supervised structural health monitoring](https://www.sciencedirect.com/science/article/pii/S0022460X18305479) (2018)                                                                                                         |
+|  3 | Poole, Gardner, Dervilis, **Bull**, Worden [On statistic alignment for domain adaptation in structural health monitoring](https://journals.sagepub.com/doi/abs/10.1177/14759217221110441) (2023)                                                                                          |
+|  5 | Hughes, **Bull**, Gardner, Dervilis, Worden [On robust risk-based active-learning algorithms for enhanced decision support](https://www.sciencedirect.com/science/article/pii/S0888327022006124) (2022)                                                                                   |
+|  6 | Dardeno, **Bull**, Mills, Dervilis, Worden [Modelling variability in vibration-based PBSHM via a generalised population form](https://www.sciencedirect.com/science/article/pii/S0022460X22004151) (2022)                                                                                 |
+|  7 | **Bull**, Dhada, Steinert, Lindgren, Parlikad, Duncan, Girolami [Knowledge Transfer in Engineering Fleets: Hierarchical Bayesian Modelling for Multi-Task Learning](https://arxiv.org/abs/2204.12404) (2022)                                                                              |
+|  8 | **Bull**, Dervilis, Worden, Cross, Rogers [A sampling-based approach for information-theoretic inspection management](https://royalsocietypublishing.org/doi/abs/10.1098/rspa.2021.0790) (2022)                                                                                           |
+| 14 | Gardner, **Bull**, Gosliga, Poole, Dervilis, Worden [A population-based SHM methodology for heterogeneous structures: Transferring damage localisation knowledge between different aircraft wings](https://www.sciencedirect.com/science/article/pii/S0888327022001030) (2022)            |
+| 15 | **Bull**, Gardner, Rogers, Dervilis, Cross, Papatheou, Maguire, Campos, Worden [Bayesian modelling of multivalued power curves from an operational wind farm](https://www.sciencedirect.com/science/article/pii/S0888327021008724) (2022)                                                 |
+| 16 | Gardner, **Bull**, Dervilis, Worden [Domain-adapted Gaussian mixture models for population-based structural health monitoring](https://link.springer.com/article/10.1007/s13349-022-00565-5) (2022)                                                                                       |
+| 18 | Gardner, **Bull**, Dervilis, Worden [On the application of kernelised Bayesian transfer learning to population-based structural health monitoring](https://www.sciencedirect.com/science/article/pii/S088832702100861X) (2022)                                                            |
+| 19 | Hughes, **Bull**, Gardner, Barthorpe, Dervilis, Worden [On risk-based active learning for structural health monitoring](https://www.sciencedirect.com/science/article/pii/S0888327021009055) (2022)                                                                                       |
+| 26 | Gardner, **Bull**, Dervilis, Worden [Overcoming the problem of repair in structural health monitoring: Metric-informed transfer learning](https://www.sciencedirect.com/science/article/pii/S0022460X21003175) (2021)                                                                     |
+| 28 | **Bull**, Gardner, Dervilis, Papatheou, Haywood-alexander, Mills, Worden [On the transfer of damage detectors between structures: An experimental case study](https://www.sciencedirect.com/science/article/pii/S0022460X21001449) (2021)                                                 |
+| 29 | **Bull**, Gardner, Rogers, Cross, Dervilis, Worden [Probabilistic inference for structural health monitoring: new modes of learning from data](https://ascelibrary.org/doi/abs/10.1061/AJRUA6.0001106) (2021)                                                                             |
+| 30 | Gardner, **Bull**, Gosliga, Dervilis, Worden [Foundations of population-based SHM, Part III: Heterogeneous populations–mapping and transfer](https://www.sciencedirect.com/science/article/pii/S0888327020305288) (2021)                                                                  |
+| 31 | **Bull**, Gardner, Gosliga, Rogers, Dervilis, Cross, Papatheou, Maguire, Campos, Worden [Foundations of population-based SHM, Part I: Homogeneous populations and forms](https://www.sciencedirect.com/science/article/pii/S0888327020305276) (2021)                                      |
+| 32 | Gosliga, Gardner, **Bull**, Dervilis, Worden [Foundations of Population-based SHM, Part II: Heterogeneous populations–Graphs, networks, and communities](https://www.sciencedirect.com/science/article/pii/S0888327020305306) (2021)                                                      |
+| 33 | Gardner, **Bull**, Gosliga, Poole, Dervilis, Worden [On a Population-Based Structural Health Monitoring Framework: An Aerospace Case Study](https://www.dpi-proceedings.com/index.php/shm2021/article/view/36243) (2021)                                                                  |
+| 34 | Dardeno, Haywood-alexander, Mills, **Bull**, Dervilis, Worden [Investigating the effects of ambient temperature on feature consistency in vibration-based SHM](https://www.dpi-proceedings.com/index.php/shm2021/article/view/36344) (2021)                                               |
+| 35 | Dardeno, **Bull**, Dervilis, Worden [Investigating experimental repeatability and feature consistency in vibration-based SHM](https://www.dpi-proceedings.com/index.php/shm2021/article/view/36346) (2021)                                                                                |
+| 36 | Poole, Gardner, Dervilis, **Bull**, Worden [On normalisation for domain adaptation in population-based structural health monitoring](https://www.dpi-proceedings.com/index.php/shm2021/article/view/36280) (2021)                                                                         |
+| 41 | Zammit, **Bull**, Sanders, Galvin, Dervilis, Sidhu, Worden [Towards the Probabilistic Analysis of Small Bowel Capsule Endoscopy Features to Predict Severity of Duodenal Histology in Patients with Villous Atrophy](https://link.springer.com/article/10.1007/s10916-020-01657-9) (2020) |
+| 42 | Worden, **Bull**, Gardner, Gosliga, Rogers, Cross, Papatheou, Lin, Dervilis [A brief introduction to recent developments in population-based structural health monitoring](https://www.frontiersin.org/articles/10.3389/fbuil.2020.00146/full) (2020)                                     |
+| 44 | **Bull**, Worden, Dervilis [Towards semi-supervised and probabilistic classification in structural health monitoring](https://www.sciencedirect.com/science/article/pii/S088832702030039X) (2020)                                                                                         |
+| 50 | **Bull**, Rogers, Wickramarachchi, Cross, Worden, Dervilis [Probabilistic active learning: an online framework for structural health monitoring](https://www.sciencedirect.com/science/article/pii/S0888327019305096) (2019)                                                              |
+| 51 | **Bull**, Worden, Fuentes, Manson, Cross, Dervilis [Outlier ensembles: A robust method for damage detection and unsupervised feature extraction from high-dimensional data](https://www.sciencedirect.com/science/article/pii/S0022460X1930197X) (2019)                                   |
+| 59 | **Bull**, Worden, Manson, Dervilis [Active learning for semi-supervised structural health monitoring](https://www.sciencedirect.com/science/article/pii/S0022460X18305479) (2018)                                                                                                         |
 
 |    | Preprints                                                                                                                                                                                                          |
-|---:|:------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------|
-|  5 | Hughes, **Bull**, Gardner, Dervilis, Worden [Mitigating sampling bias in risk-based active learning via an EM algorithm](https://arxiv.org/abs/2206.12598) (2022)                               |
-|  6 | Dardeno, **Bull**, Dervilis, Worden [A generalised form for a homogeneous population of structures using an overlapping mixture of Gaussian processes](https://arxiv.org/abs/2206.11683) (2022) |
-|  7 | Hughes, Gardner, **Bull**, Dervilis, Worden [Improving decision-making via risk-based active learning: Probabilistic discriminative classifiers](https://arxiv.org/abs/2206.11616) (2022)       |
-|  9 | Poole, Gardner, Dervilis, **Bull**, Worden [On statistic alignment for domain adaptation in structural health monitoring](https://arxiv.org/abs/2205.12052) (2022)                              |
-| 15 | Dardeno, **Bull**, Mills, Dervilis, Worden [Modelling variability in vibration-based PBSHM via a generalised population form](https://arxiv.org/abs/2203.07115) (2022)                          |
-| 16 | Hughes, **Bull**, Gardner, Dervilis, Worden [On robust risk-based active-learning algorithms for enhanced decision support](https://arxiv.org/abs/2201.02555) (2022)                            |
+|---:|:-------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------|
+|  1 | Bee, **Bull**, Dervilis, Worden [When is an SHM problem a Multi-Task-Learning problem?](https://arxiv.org/abs/2305.09425) (2023)                                                                                   |
+|  2 | **Bull**, Jones, Cross, Duncan, Girolami [Encoding Domain Expertise into Multilevel Models for Source Location](https://arxiv.org/abs/2305.08657) (2023)                                                           |
+|  4 | Bee, Papatheou, Haywood-alexander, Mills, **Bull**, Worden, Dervilis [Better Together: Using Multi-task Learning to Improve Feature Selection within Structural Datasets](https://arxiv.org/abs/2303.04486) (2023) |
+|  9 | Hughes, **Bull**, Gardner, Dervilis, Worden [Mitigating sampling bias in risk-based active learning via an EM algorithm](https://arxiv.org/abs/2206.12598) (2022)                                                  |
+| 10 | Dardeno, **Bull**, Dervilis, Worden [A generalised form for a homogeneous population of structures using an overlapping mixture of Gaussian processes](https://arxiv.org/abs/2206.11683) (2022)                    |
+| 11 | Hughes, Gardner, **Bull**, Dervilis, Worden [Improving decision-making via risk-based active learning: Probabilistic discriminative classifiers](https://arxiv.org/abs/2206.11616) (2022)                          |
 
@@
 |---:|:------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------|
-| 20 | **Bull**, Hughes, Rogers, Gardner, Worden, Dervilis [Partially Supervised Learning for Data-Driven Structural Health Monitoring](https://link.springer.com/chapter/10.1007/978-3-030-81716-9_19) (2022)                       |
-| 21 | Gardner, **Bull**, Gosliga, Dervilis, Cross, Papatheou, Worden [Population-Based Structural Health Monitoring](https://link.springer.com/chapter/10.1007/978-3-030-81716-9_20) (2022)                                         |
-| 41 | Fuentes, Cross, Gardner, **Bull**, Rogers, Barthorpe, Shi, Dervilis, Farrar, Worden [Structural Health Monitoring and Damage Identification](https://link.springer.com/content/pdf/10.1007/978-1-4939-6503-8_23-1.pdf) (2020) |
+| 21 | **Bull**, Hughes, Rogers, Gardner, Worden, Dervilis [Partially Supervised Learning for Data-Driven Structural Health Monitoring](https://link.springer.com/chapter/10.1007/978-3-030-81716-9_19) (2022)                       |
+| 22 | Gardner, **Bull**, Gosliga, Dervilis, Cross, Papatheou, Worden [Population-Based Structural Health Monitoring](https://link.springer.com/chapter/10.1007/978-3-030-81716-9_20) (2022)                                         |
+| 45 | Fuentes, Cross, Gardner, **Bull**, Rogers, Barthorpe, Shi, Dervilis, Farrar, Worden [Structural Health Monitoring and Damage Identification](https://link.springer.com/content/pdf/10.1007/978-1-4939-6503-8_23-1.pdf) (2020) |
 
@@
 |---:|:--------------------------------------------------------------------------------------------------------------------------------------|
-| 51 | **Bull** [Towards probabilistic and partially-supervised structural health monitoring](https://etheses.whiterose.ac.uk/26282/) (2019) |
+| 55 | **Bull** [Towards probabilistic and partially-supervised structural health monitoring](https://etheses.whiterose.ac.uk/26282/) (2019) |
 
 |    | Conference papers                                                                                                                                                                                                                                                                                                                                                                               |
-|---:|:---------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------|
-|  1 | Poole, Gardner, Dervilis, **Bull**, Worden [On the Application of Partial Domain Adaptation for PBSHM](https://link.springer.com/chapter/10.1007/978-3-031-07322-9_42) (2023)                                                                                                                                                                                              |
-|  2 | Dhada, **Bull**, Girolami, Parlikad [Modelling the Times-to-Failures Using a Statistical Hierarchical Model](https://link.springer.com/chapter/10.1007/978-3-031-07258-1_99) (2023)                                                                                                                                                                                        |
-| 12 | **Bull**, Dhada, Steinert, Lindgren, Parlikad, Girolami [Population-Level Modelling for Truck Fleet Survival Analysis](https://aspace.repository.cam.ac.uk/handle/1810/335452) (2022)                                                                                                                                                                                      |
-| 17 | Hughes, **Bull**, Gardner, Dervilis, Worden, Hughes [Semi-supervised risk-based active learning using inspection and maintenance information](https://eprints.whiterose.ac.uk/191598/) (2022)                                                                                                                                                                              |
-| 22 | Gardner, **Bull**, Dervilis, Worden [Challenges for SHM from Structural Repairs: An Outlier-Informed Domain Adaptation Approach](https://link.springer.com/chapter/10.1007/978-3-030-76004-5_10) (2022)                                                                                                                                                                    |
-| 23 | Gardner, **Bull**, Dervilis, Worden [On the Application of Heterogeneous Transfer Learning to Population-Based Structural Health Monitoring](https://link.springer.com/chapter/10.1007/978-3-030-76004-5_11) (2022)                                                                                                                                                        |
-| 24 | **Bull**, Gardner, Dervilis, Papatheou, Haywood-Alexander, Mills, Worden [Transferring Damage Detectors Between Tailplane Experiments](https://link.springer.com/chapter/10.1007/978-3-030-76004-5_22) (2022)                                                                                                                                                              |
-| 26 | Hughes, **Bull**, Gardner, Barthorpe, Dervilis, Worden [A risk-based active learning approach to inspection scheduling](https://www.researchgate.net/profile/Aidan-Hughes-4/publication/355903488_A_risk-based_active_learning_approach_to_inspection_scheduling/links/61892373d7d1af224bc69a96/A-risk-based-active-learning-approach-to-inspection-scheduling.pdf) (2021) |
-| 33 | **Bull**, Gardner, Dervilis, Papatheou, Worden [Automated Feature Extraction for Damage Detection: A Pseudo-fault Framework for Population-based SHM]() (2021)                                                                                                                                                                                                             |
-| 34 | **Bull**, Gardner, Dervilis, Worden [Normalising Flows and Nonlinear Normal Modes](https://www.sciencedirect.com/science/article/pii/S240589632101209X) (2021)                                                                                                                                                                                                             |
-| 35 | Gosliga, Gardner, **Bull**, Dervilis, Worden [Towards population-based structural health monitoring, Part III: Graphs, networks and communities](https://link.springer.com/chapter/10.1007/978-3-030-47717-2_26) (2021)                                                                                                                                                    |
-| 36 | Gosliga, Gardner, **Bull**, Dervilis, Worden [Towards population-based structural health monitoring, Part II: heterogeneous populations and structures as graphs](https://link.springer.com/chapter/10.1007/978-3-030-47717-2_17) (2021)                                                                                                                                   |
-| 39 | **Bull**, Gardner, Rogers, Cross, Dervilis, Worden [New Modes of Inference for Probabilistic SHM](https://link.springer.com/chapter/10.1007/978-3-030-64908-1_39) (2020)                                                                                                                                                                                                   |
-| 42 | Gardner, **Bull**, Gosliga, Dervilis, Worden [Towards population-based structural health monitoring, Part IV: heterogeneous populations, transfer and mapping](https://link.springer.com/chapter/10.1007/978-3-030-47638-0_20) (2020)                                                                                                                                      |
-| 43 | Gardner, **Bull**, Dervilis, Worden [Kernelised Bayesian transfer learning for population-based structural health monitoring](https://link.springer.com/chapter/10.1007/978-3-030-47638-0_22) (2020)                                                                                                                                                                       |
-| 44 | **Bull**, Gardner, Gosliga, Dervilis, Papatheou, Maguire, Campos, Rogers, Cross, Worden [Towards population-based structural health monitoring, Part I: Homogeneous populations and forms](https://link.springer.com/chapter/10.1007/978-3-030-47638-0_32) (2020)                                                                                                          |
-| 45 | **Bull**, Worden, Rogers, Cross, Dervilis [Investigating engineering data by probabilistic measures](https://link.springer.com/chapter/10.1007/978-3-030-12243-0_12) (2020)                                                                                                                                                                                                |
-| 48 | **Bull**, Worden, Rogers, Wickramarachchi, Cross, McLeay, Leahy, Dervilis [A probabilistic framework for online structural health monitoring: active learning from machining data streams](https://iopscience.iop.org/article/10.1088/1742-6596/1264/1/012028/meta) (2019)                                                                                                 |
-| 49 | **Bull**, Rogers, Dervilis, Cross, Worden [A Gaussian process form for population-based structural health monitoring](https://eprints.whiterose.ac.uk/148168/) (2019)                                                                                                                                                                                                      |
-| 50 | **Bull**, Dervilis, Worden [Experimental Validation of the Population-Form to Represent Nominally-Identical Systems](https://scholar.google.com/scholar?cluster=7507461710880003650&hl=en&oi=scholarr) (2019)                                                                                                                                                              |
-| 52 | **Bull**, Worden, Dervilis [Damage classification using labelled and unlabelled measurements](https://www.researchgate.net/profile/Lawrence-Bull-2/publication/337303717_Damage_Classification_Using_Labelled_and_Unlabelled_Measurements/links/62276fc93c53d31ba4b15c45/Damage-Classification-Using-Labelled-and-Unlabelled-Measurements.pdf) (2019)                      |
-| 53 | Dervilis, Zhang, **Bull**, Cross, Rogers, Fuentes, Dertimanis, Abdallah, Chatzi, Worden [A nonlinear robust outlier detection approach for SHM](https://eprints.whiterose.ac.uk/147321/) (2019)                                                                                                                                                                            |
-| 54 | **Bull**, Manson, Worden, Dervilis [Active Learning Approaches to Structural Health Monitoring](https://link.springer.com/chapter/10.1007/978-3-319-75390-4_14) (2019)                                                                                                                                                                                                     |
-| 56 | **Bull**, Worden, Cross, Dervilis [Outlier Ensembles: an Alternative Robust Method for Inclusive Outlier Analysis with Structural Health Monitoring Data]() (2018)                                                                                                                                                                                                         |
+|---:|:------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------|
+| 12 | Poole, Gardner, Dervilis, **Bull**, Worden [On the Application of Partial Domain Adaptation for PBSHM](https://link.springer.com/chapter/10.1007/978-3-031-07322-9_42) (2022)                                                                                                                                                                                                                   |
+| 13 | Dhada, **Bull**, Girolami, Parlikad [Modelling the Times-to-Failures Using a Statistical Hierarchical Model](https://link.springer.com/chapter/10.1007/978-3-031-07258-1_99) (2022)                                                                                                                                                                                                             |
+| 17 | **Bull**, Dhada, Steinert, Lindgren, Parlikad, Girolami [Population-Level Modelling for Truck Fleet Survival Analysis](https://www.repository.cam.ac.uk/bitstreams/905dbe0a-1a73-4fc5-861f-9ff7a9c816c9/download) (2022)                                                                                                                                                                        |
+| 20 | Hughes, **Bull**, Gardner, Dervilis, Worden, Hughes [Semi-supervised risk-based active learning using inspection and maintenance information](https://eprints.whiterose.ac.uk/191598/) (2022)                                                                                                                                                                                                   |
+| 23 | Gardner, **Bull**, Dervilis, Worden [Challenges for SHM from Structural Repairs: An Outlier-Informed Domain Adaptation Approach](https://link.springer.com/chapter/10.1007/978-3-030-76004-5_10) (2022)                                                                                                                                                                                         |
+| 24 | Gardner, **Bull**, Dervilis, Worden [On the Application of Heterogeneous Transfer Learning to Population-Based Structural Health Monitoring](https://link.springer.com/chapter/10.1007/978-3-030-76004-5_11) (2022)                                                                                                                                                                             |
+| 25 | **Bull**, Gardner, Dervilis, Papatheou, Haywood-alexander, Mills, Worden [Transferring Damage Detectors Between Tailplane Experiments](https://link.springer.com/chapter/10.1007/978-3-030-76004-5_22) (2022)                                                                                                                                                                                   |
+| 27 | Hughes, **Bull**, Gardner, Barthorpe, Dervilis, Worden [A risk-based active learning approach to inspection scheduling](https://www.researchgate.net/profile/Aidan-Hughes-4/publication/355903488_A_risk-based_active_learning_approach_to_inspection_scheduling/links/61892373d7d1af224bc69a96/A-risk-based-active-learning-approach-to-inspection-scheduling.pdf) (2021)                      |
+| 37 | **Bull**, Gardner, Dervilis, Papatheou, Worden [Automated Feature Extraction for Damage Detection: A Pseudo-fault Framework for Population-based SHM]() (2021)                                                                                                                                                                                                                                  |
+| 38 | **Bull**, Gardner, Dervilis, Worden [Normalising Flows and Nonlinear Normal Modes](https://www.sciencedirect.com/science/article/pii/S240589632101209X) (2021)                                                                                                                                                                                                                                  |
+| 39 | Gosliga, Gardner, **Bull**, Dervilis, Worden [Towards population-based structural health monitoring, Part III: Graphs, networks and communities](https://link.springer.com/chapter/10.1007/978-3-030-47717-2_26) (2021)                                                                                                                                                                         |
+| 40 | Gosliga, Gardner, **Bull**, Dervilis, Worden [Towards population-based structural health monitoring, Part II: heterogeneous populations and structures as graphs](https://link.springer.com/chapter/10.1007/978-3-030-47717-2_17) (2021)                                                                                                                                                        |
+| 43 | **Bull**, Gardner, Rogers, Cross, Dervilis, Worden [New Modes of Inference for Probabilistic SHM](https://link.springer.com/chapter/10.1007/978-3-030-64908-1_39) (2020)                                                                                                                                                                                                                        |
+| 46 | Gardner, **Bull**, Gosliga, Dervilis, Worden [Towards population-based structural health monitoring, Part IV: heterogeneous populations, transfer and mapping](https://link.springer.com/chapter/10.1007/978-3-030-47638-0_20) (2020)                                                                                                                                                           |
+| 47 | Gardner, **Bull**, Dervilis, Worden [Kernelised Bayesian transfer learning for population-based structural health monitoring](https://link.springer.com/chapter/10.1007/978-3-030-47638-0_22) (2020)                                                                                                                                                                                            |
+| 48 | **Bull**, Gardner, Gosliga, Dervilis, Papatheou, Maguire, Campos, Rogers, Cross, Worden [Towards population-based structural health monitoring, Part I: Homogeneous populations and forms](https://link.springer.com/chapter/10.1007/978-3-030-47638-0_32) (2020)                                                                                                                               |
+| 49 | **Bull**, Worden, Rogers, Cross, Dervilis [Investigating engineering data by probabilistic measures](https://link.springer.com/chapter/10.1007/978-3-030-12243-0_12) (2020)                                                                                                                                                                                                                     |
+| 52 | **Bull**, Worden, Rogers, Wickramarachchi, Cross, Mcleay, Leahy, Dervilis [A probabilistic framework for online structural health monitoring: active learning from machining data streams](https://iopscience.iop.org/article/10.1088/1742-6596/1264/1/012028/meta) (2019)                                                                                                                      |
+| 53 | **Bull**, Rogers, Dervilis, Cross, Worden [A Gaussian process form for population-based structural health monitoring](https://www.researchgate.net/profile/Lawrence-Bull-2/publication/334250549_A_Gaussian_process_form_for_population-based_structural_health_monitoring/links/622771023c53d31ba4b15c72/A-Gaussian-process-form-for-population-based-structural-health-monitoring.pdf) (2019) |
+| 54 | **Bull**, Dervilis, Worden [Experimental Validation of the Population-Form to Represent Nominally-Identical Systems](https://www.dpi-proceedings.com/index.php/shm2019/article/view/32373) (2019)                                                                                                                                                                                               |
+| 56 | **Bull**, Worden, Dervilis [Damage classification using labelled and unlabelled measurements](https://www.researchgate.net/profile/Lawrence-Bull-2/publication/337303717_Damage_Classification_Using_Labelled_and_Unlabelled_Measurements/links/62276fc93c53d31ba4b15c45/Damage-Classification-Using-Labelled-and-Unlabelled-Measurements.pdf) (2019)                                           |
+| 57 | Dervilis, Zhang, **Bull**, Cross, Rogers, Fuentes, Dertimanis, Abdallah, Chatzi, Worden [A nonlinear robust outlier detection approach for SHM](https://eprints.whiterose.ac.uk/147321/) (2019)                                                                                                                                                                                                 |
+| 58 | **Bull**, Manson, Worden, Dervilis [Active Learning Approaches to Structural Health Monitoring](https://link.springer.com/chapter/10.1007/978-3-319-75390-4_14) (2019)                                                                                                                                                                                                                          |
+| 60 | **Bull**, Worden, Cross, Dervilis [Outlier Ensembles: an Alternative Robust Method for Inclusive Outlier Analysis with Structural Health Monitoring Data]() (2018)                                                                                                                                                                                                                              |
 

### 2024-04-02 index.qmd
glasgow

@@
 
-**[2022-2027] University of Cambridge** | [Computational Statistics and Machine Learning Group](https://csml-cam.github.io) | Research Associate | Department of Engineering
+**[May.2024-May.2027] University of Glasgow** | Research Fellow | [Statistics & Data Analytics](https://www.gla.ac.uk/schools/mathematicsstatistics/research/stats/ai3/) | School of Mathematics and Statistics
 
-**[2021-2022] The Alan Turing Institute** | Research Associate | [Data-Centric Engineering](https://www.turing.ac.uk/research/research-programmes/data-centric-engineering)
+**[Sep.2022-May.2024] University of Cambridge** | Research Associate | [Computational Statistics and Machine Learning Group](https://csml-cam.github.io) | Department of Engineering
 
-**[2016-2021] University of Sheffield** | PhD Student (2016-2019) Research Assistant (2019-2022) | [Dynamics Research Group](https://drg.ac.uk/) | Department of Engineering
+**[Jul.2021-Sep.2022] The Alan Turing Institute** | Research Associate | [Data-Centric Engineering](https://www.turing.ac.uk/research/research-programmes/data-centric-engineering)
+
+**[Sep.2016-Jun.2021] University of Sheffield** | PhD Student (2016-2019) Research Assistant (2019-2021) | [Dynamics Research Group](https://drg.ac.uk/) | Department of Engineering
 
@@
 
-Broadly speaking, I'm a researcher in statistical methods for Data-Centric Engineering. Focussing on monitoring techniques for telemetry data from systems and infrastructure.
+Researcher in statistical methods for Data-Centric Engineering, specialising in monitoring techniques for telemetry data from systems and infrastructure.
 
-I'm particularly interested in _multilevel structures_ that appear in measurements from populations of systems -- trains, [planes](https://www.sciencedirect.com/science/article/pii/S0022460X21001449), [automobiles](https://doi.org/10.48550/arXiv.2204.12404) (...
+I'm interested in the dependencies that appear in measurements from populations of machines -- [planes](https://www.sciencedirect.com/science/article/pii/S0022460X21001449), [trains](https://arxiv.org/abs/2403.17820), [automobiles](https://doi.org/10.48550/arXiv.2204.12404) (...
 [wind turbines](https://arxiv.org/abs/2111.15496)).
-By encoding domain expertise in a Bayesian workflow, complex models can be built from interpretable units, allowing machines to share information and increasing the value of data.
-At the population level, alternative insights can emerge that might otherwise be missed -- the whole is something _besides_ its parts.
+By encoding domain expertise into statistical models, complex representations can be built from interpretable units, allowing machines to share information and increase the value of data.
+<!-- At a systems level, alternative insights can emerge that might otherwise be missed -- the whole is something _besides_ its parts. -->
 
-I'm a communications editor for the [Data-Centric Engineering](https://www.cambridge.org/core/journals/data-centric-engineering) journal (Cambridge University Press) and a member of the [Early-Career Academic and Professionals Panel](https://www-smartinfrastructure.eng.cam.ac.uk/news/csic-call-applicants-early-career-academics-and-professionals-panel) (ECAPP) in the [Cambridge Centre for Smart Infrastructure and Construction](https://www-smartinfrastructure.eng.cam.ac.uk/) (CSIC).
+I'm a communications editor for the [Data-Centric Engineering](https://www.cambridge.org/core/journals/data-centric-engineering) journal and a Visiting Research Fellow at [Cambridge University](https://csml-cam.github.io).
+I was on the [Early-Career Academic and Professionals Panel](https://www-smartinfrastructure.eng.cam.ac.uk/news/csic-call-applicants-early-career-academics-and-professionals-panel) (2021-2023) in the [Cambridge Centre for Smart Infrastructure and Construction](https://www-smartinfrastructure.eng.cam.ac.uk/) (CSIC).
 

### 2024-04-02 papers.qmd
glasgow

--- 2023-01-15 papers.qmd
@@
 |---:|:------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------|
-|  3 | **Bull**, Dhada, Steinert, Lindgren, Parlikad, Duncan, Girolami [Knowledge Transfer in Engineering Fleets: Hierarchical Bayesian Modelling for Multi-Task Learning](https://arxiv.org/abs/2204.12404) (2022)                                                                              |
-|  4 | **Bull**, Dervilis, Worden, Cross, Rogers [A sampling-based approach for information-theoretic inspection management](https://royalsocietypublishing.org/doi/abs/10.1098/rspa.2021.0790) (2022)                                                                                           |
-|  8 | Gardner, **Bull**, Gosliga, Poole, Dervilis, Worden [A population-based SHM methodology for heterogeneous structures: Transferring damage localisation knowledge between different aircraft wings](https://www.sciencedirect.com/science/article/pii/S0888327022001030) (2022)            |
-| 10 | **Bull**, Gardner, Rogers, Dervilis, Cross, Papatheou, Maguire, Campos, Worden [Bayesian modelling of multivalued power curves from an operational wind farm](https://www.sciencedirect.com/science/article/pii/S0888327021008724) (2022)                                                 |
-| 11 | Gardner, **Bull**, Dervilis, Worden [Domain-adapted Gaussian mixture models for population-based structural health monitoring](https://link.springer.com/article/10.1007/s13349-022-00565-5) (2022)                                                                                       |
-| 13 | Gardner, **Bull**, Dervilis, Worden [On the application of kernelised Bayesian transfer learning to population-based structural health monitoring](https://www.sciencedirect.com/science/article/pii/S088832702100861X) (2022)                                                            |
-| 14 | Hughes, **Bull**, Gardner, Barthorpe, Dervilis, Worden [On risk-based active learning for structural health monitoring](https://www.sciencedirect.com/science/article/pii/S0888327021009055) (2022)                                                                                       |
-| 18 | Dardeno, Haywood-Alexander, Mills, **Bull**, Dervilis, Worden [Investigating the effects of ambient temperature on feature consistency in vibration-based SHM](https://scholar.google.com/scholar?cluster=624769372939145628&hl=en&oi=scholarr) (2022)                                    |
-| 19 | Dardeno, **Bull**, Dervilis, Worden [Investigating experimental repeatability and feature consistency in vibration-based SHM](https://scholar.google.com/scholar?cluster=10140930682997029543&hl=en&oi=scholarr) (2022)                                                                   |
-| 25 | Gardner, **Bull**, Dervilis, Worden [Overcoming the problem of repair in structural health monitoring: Metric-informed transfer learning](https://www.sciencedirect.com/science/article/pii/S0022460X21003175) (2021)                                                                     |
-| 27 | **Bull**, Gardner, Dervilis, Papatheou, Haywood-Alexander, Mills, Worden [On the transfer of damage detectors between structures: an experimental case study](https://www.sciencedirect.com/science/article/pii/S0022460X21001449) (2021)                                                 |
-| 28 | **Bull**, Gardner, Rogers, Cross, Dervilis, Worden [Probabilistic inference for structural health monitoring: new modes of learning from data](https://ascelibrary.org/doi/abs/10.1061/AJRUA6.0001106) (2021)                                                                             |
-| 29 | Gardner, **Bull**, Gosliga, Dervilis, Worden [Foundations of population-based SHM, Part III: Heterogeneous populations–Mapping and transfer](https://www.sciencedirect.com/science/article/pii/S0888327020305288) (2021)                                                                  |
-| 30 | **Bull**, Gardner, Gosliga, Rogers, Dervilis, Cross, Papatheou, Maguire, Campos, Worden [Foundations of population-based SHM, Part I: Homogeneous populations and forms](https://www.sciencedirect.com/science/article/pii/S0888327020305276) (2021)                                      |
-| 31 | Gosliga, Gardner, **Bull**, Dervilis, Worden [Foundations of Population-based SHM, Part II: Heterogeneous populations–Graphs, networks, and communities](https://www.sciencedirect.com/science/article/pii/S0888327020305306) (2021)                                                      |
-| 32 | Poole, Gardner, Dervilis, **Bull**, Worden [On normalisation for domain adaptation in population-based structural health monitoring](https://scholar.google.com/scholar?cluster=9278611934387106844&hl=en&oi=scholarr) (2021)                                                             |
-| 37 | Zammit, **Bull**, Sanders, Galvin, Dervilis, Sidhu, Worden [Towards the Probabilistic Analysis of Small Bowel Capsule Endoscopy Features to Predict Severity of Duodenal Histology in Patients with Villous Atrophy](https://link.springer.com/article/10.1007/s10916-020-01657-9) (2020) |
-| 38 | Worden, **Bull**, Gardner, Gosliga, Rogers, Cross, Papatheou, Lin, Dervilis [A brief introduction to recent developments in population-based structural health monitoring](https://www.frontiersin.org/articles/10.3389/fbuil.2020.00146/full) (2020)                                     |
-| 40 | **Bull**, Worden, Dervilis [Towards semi-supervised and probabilistic classification in structural health monitoring](https://www.sciencedirect.com/science/article/pii/S088832702030039X) (2020)                                                                                         |
-| 46 | **Bull**, Rogers, Wickramarachchi, Cross, Worden, Dervilis [Probabilistic active learning: an online framework for structural health monitoring](https://www.sciencedirect.com/science/article/pii/S0888327019305096) (2019)                                                              |
-| 47 | **Bull**, Worden, Fuentes, Manson, Cross, Dervilis [Outlier ensembles: A robust method for damage detection and unsupervised feature extraction from high-dimensional data](https://www.sciencedirect.com/science/article/pii/S0022460X1930197X) (2019)                                   |
-| 55 | **Bull**, Worden, Manson, Dervilis [Active learning for semi-supervised structural health monitoring](https://www.sciencedirect.com/science/article/pii/S0022460X18305479) (2018)                                                                                                         |
+|  6 | Poole, Gardner, Dervilis, **Bull**, Worden [On statistic alignment for domain adaptation in structural health monitoring](https://journals.sagepub.com/doi/abs/10.1177/14759217221110441) (2023)                                                                                          |
+|  8 | Gardner, **Bull**, Dervilis, Worden [Domain-adapted Gaussian mixture models for population-based structural health monitoring](https://link.springer.com/article/10.1007/s13349-022-00565-5) (2022)                                                                                       |
+|  9 | Hughes, **Bull**, Gardner, Dervilis, Worden [On robust risk-based active-learning algorithms for enhanced decision support](https://www.sciencedirect.com/science/article/pii/S0888327022006124) (2022)                                                                                   |
+| 10 | Dardeno, **Bull**, Mills, Dervilis, Worden [Modelling variability in vibration-based PBSHM via a generalised population form](https://www.sciencedirect.com/science/article/pii/S0022460X22004151) (2022)                                                                                 |
+| 11 | **Bull**, Dhada, Steinert, Lindgren, Parlikad, Duncan, Girolami [Knowledge Transfer in Engineering Fleets: Hierarchical Bayesian Modelling for Multi-Task Learning](https://arxiv.org/abs/2204.12404) (2022)                                                                              |
+| 12 | **Bull**, Dervilis, Worden, Cross, Rogers [A sampling-based approach for information-theoretic inspection management](https://royalsocietypublishing.org/doi/abs/10.1098/rspa.2021.0790) (2022)                                                                                           |
+| 18 | Gardner, **Bull**, Gosliga, Poole, Dervilis, Worden [A population-based SHM methodology for heterogeneous structures: Transferring damage localisation knowledge between different aircraft wings](https://www.sciencedirect.com/science/article/pii/S0888327022001030) (2022)            |
+| 19 | **Bull**, Gardner, Rogers, Dervilis, Cross, Papatheou, Maguire, Campos, Worden [Bayesian modelling of multivalued power curves from an operational wind farm](https://www.sciencedirect.com/science/article/pii/S0888327021008724) (2022)                                                 |
+| 21 | Gardner, **Bull**, Dervilis, Worden [On the application of kernelised Bayesian transfer learning to population-based structural health monitoring](https://www.sciencedirect.com/science/article/pii/S088832702100861X) (2022)                                                            |
+| 22 | Hughes, **Bull**, Gardner, Barthorpe, Dervilis, Worden [On risk-based active learning for structural health monitoring](https://www.sciencedirect.com/science/article/pii/S0888327021009055) (2022)                                                                                       |
+| 29 | Gardner, **Bull**, Dervilis, Worden [Overcoming the problem of repair in structural health monitoring: Metric-informed transfer learning](https://www.sciencedirect.com/science/article/pii/S0022460X21003175) (2021)                                                                     |
+| 31 | **Bull**, Gardner, Dervilis, Papatheou, Haywood-alexander, Mills, Worden [On the transfer of damage detectors between structures: An experimental case study](https://www.sciencedirect.com/science/article/pii/S0022460X21001449) (2021)                                                 |
+| 32 | **Bull**, Gardner, Rogers, Cross, Dervilis, Worden [Probabilistic inference for structural health monitoring: new modes of learning from data](https://ascelibrary.org/doi/abs/10.1061/AJRUA6.0001106) (2021)                                                                             |
+| 33 | Gardner, **Bull**, Gosliga, Dervilis, Worden [Foundations of population-based SHM, Part III: Heterogeneous populations–Mapping and transfer](https://www.sciencedirect.com/science/article/pii/S0888327020305288) (2021)                                                                  |
+| 34 | **Bull**, Gardner, Gosliga, Rogers, Dervilis, Cross, Papatheou, Maguire, Campos, Worden [Foundations of population-based SHM, Part I: Homogeneous populations and forms](https://www.sciencedirect.com/science/article/pii/S0888327020305276) (2021)                                      |
+| 35 | Gosliga, Gardner, **Bull**, Dervilis, Worden [Foundations of Population-based SHM, Part II: Heterogeneous populations–Graphs, networks, and communities](https://www.sciencedirect.com/science/article/pii/S0888327020305306) (2021)                                                      |
+| 36 | Gardner, **Bull**, Gosliga, Poole, Dervilis, Worden [On a Population-Based Structural Health Monitoring Framework: An Aerospace Case Study](https://www.dpi-proceedings.com/index.php/shm2021/article/view/36243) (2021)                                                                  |
+| 37 | Dardeno, Haywood-alexander, Mills, **Bull**, Dervilis, Worden [Investigating the effects of ambient temperature on feature consistency in vibration-based SHM](https://www.dpi-proceedings.com/index.php/shm2021/article/view/36344) (2021)                                               |
+| 38 | Dardeno, **Bull**, Dervilis, Worden [Investigating experimental repeatability and feature consistency in vibration-based SHM](https://www.dpi-proceedings.com/index.php/shm2021/article/view/36346) (2021)                                                                                |
+| 39 | Poole, Gardner, Dervilis, **Bull**, Worden [On normalisation for domain adaptation in population-based structural health monitoring](https://www.dpi-proceedings.com/index.php/shm2021/article/view/36280) (2021)                                                                         |
+| 44 | Zammit, **Bull**, Sanders, Galvin, Dervilis, Sidhu, Worden [Towards the Probabilistic Analysis of Small Bowel Capsule Endoscopy Features to Predict Severity of Duodenal Histology in Patients with Villous Atrophy](https://link.springer.com/article/10.1007/s10916-020-01657-9) (2020) |
+| 45 | Worden, **Bull**, Gardner, Gosliga, Rogers, Cross, Papatheou, Lin, Dervilis [A brief introduction to recent developments in population-based structural health monitoring](https://www.frontiersin.org/articles/10.3389/fbuil.2020.00146/full) (2020)                                     |
+| 47 | **Bull**, Worden, Dervilis [Towards semi-supervised and probabilistic classification in structural health monitoring](https://www.sciencedirect.com/science/article/pii/S088832702030039X) (2020)                                                                                         |
+| 53 | **Bull**, Rogers, Wickramarachchi, Cross, Worden, Dervilis [Probabilistic active learning: An online framework for structural health monitoring](https://www.sciencedirect.com/science/article/pii/S0888327019305096) (2019)                                                              |
+| 54 | **Bull**, Worden, Fuentes, Manson, Cross, Dervilis [Outlier ensembles: A robust method for damage detection and unsupervised feature extraction from high-dimensional data](https://www.sciencedirect.com/science/article/pii/S0022460X1930197X) (2019)                                   |
+| 62 | **Bull**, Worden, Manson, Dervilis [Active learning for semi-supervised structural health monitoring](https://www.sciencedirect.com/science/article/pii/S0022460X18305479) (2018)                                                                                                         |
 
 |    | Preprints                                                                                                                                                                                                          |
-|---:|:------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------|
-|  5 | Hughes, **Bull**, Gardner, Dervilis, Worden [Mitigating sampling bias in risk-based active learning via an EM algorithm](https://arxiv.org/abs/2206.12598) (2022)                               |
-|  6 | Dardeno, **Bull**, Dervilis, Worden [A generalised form for a homogeneous population of structures using an overlapping mixture of Gaussian processes](https://arxiv.org/abs/2206.11683) (2022) |
-|  7 | Hughes, Gardner, **Bull**, Dervilis, Worden [Improving decision-making via risk-based active learning: Probabilistic discriminative classifiers](https://arxiv.org/abs/2206.11616) (2022)       |
-|  9 | Poole, Gardner, Dervilis, **Bull**, Worden [On statistic alignment for domain adaptation in structural health monitoring](https://arxiv.org/abs/2205.12052) (2022)                              |
-| 15 | Dardeno, **Bull**, Mills, Dervilis, Worden [Modelling variability in vibration-based PBSHM via a generalised population form](https://arxiv.org/abs/2203.07115) (2022)                          |
-| 16 | Hughes, **Bull**, Gardner, Dervilis, Worden [On robust risk-based active-learning algorithms for enhanced decision support](https://arxiv.org/abs/2201.02555) (2022)                            |
+|---:|:-------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------|
+|  2 | Dardeno, Mills, Dervilis, Worden, **Bull** [On the hierarchical Bayesian modelling of frequency response functions](https://arxiv.org/abs/2307.06263) (2023)                                                       |
+|  4 | Bee, **Bull**, Dervilis, Worden [When is an SHM problem a Multi-Task-Learning problem?](https://arxiv.org/abs/2305.09425) (2023)                                                                                   |
+|  5 | **Bull**, Jones, Cross, Duncan, Girolami [Encoding Domain Expertise into Multilevel Models for Source Location](https://arxiv.org/abs/2305.08657) (2023)                                                           |
+|  7 | Bee, Papatheou, Haywood-alexander, Mills, **Bull**, Worden, Dervilis [Better Together: Using Multi-task Learning to Improve Feature Selection within Structural Datasets](https://arxiv.org/abs/2303.04486) (2023) |
+| 13 | Hughes, **Bull**, Gardner, Dervilis, Worden [Mitigating sampling bias in risk-based active learning via an EM algorithm](https://arxiv.org/abs/2206.12598) (2022)                                                  |
+| 14 | Dardeno, **Bull**, Dervilis, Worden [A generalised form for a homogeneous population of structures using an overlapping mixture of Gaussian processes](https://arxiv.org/abs/2206.11683) (2022)                    |
+| 15 | Hughes, Gardner, **Bull**, Dervilis, Worden [Improving decision-making via risk-based active learning: Probabilistic discriminative classifiers](https://arxiv.org/abs/2206.11616) (2022)                          |
 
 |    | Book chapters                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                       |
-|---:|:------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------|
-| 20 | **Bull**, Hughes, Rogers, Gardner, Worden, Dervilis [Partially Supervised Learning for Data-Driven Structural Health Monitoring](https://link.springer.com/chapter/10.1007/978-3-030-81716-9_19) (2022)                       |
-| 21 | Gardner, **Bull**, Gosliga, Dervilis, Cross, Papatheou, Worden [Population-Based Structural Health Monitoring](https://link.springer.com/chapter/10.1007/978-3-030-81716-9_20) (2022)                                         |
-| 41 | Fuentes, Cross, Gardner, **Bull**, Rogers, Barthorpe, Shi, Dervilis, Farrar, Worden [Structural Health Monitoring and Damage Identification](https://link.springer.com/content/pdf/10.1007/978-1-4939-6503-8_23-1.pdf) (2020) |
+|---:|:--------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------|
+|  1 | **Bull**, Abdallah, Mylonas, Avendaño-valencia, Tatsis, Gardner, Rogers, Brennan, Cross, Worden, Duncan, Dervilis, Girolami, Chatzi [Data-Centric Monitoring of Wind Farms](https://books.google.com/books?hl=en&lr=&id=x57WEAAAQBAJ&oi=fnd&pg=PA206&dq=info:opW30yPHEQIJ:scholar.google.com&ots=4gPsEjkVJD&sig=Bt-r4xbjSNrN1u56wv-z15xIEYI) (2023)                                                                                                                                                                                                                 |
+| 24 | **Bull**, Hughes, Rogers, Gardner, Worden, Dervilis [Partially Supervised Learning for Data-Driven Structural Health Monitoring](https://link.springer.com/chapter/10.1007/978-3-030-81716-9_19) (2022)                                                                                                                                                                                                                                                                                                                                                             |
+| 25 | Gardner, **Bull**, Gosliga, Dervilis, Cross, Papatheou, Worden [Population-Based Structural Health Monitoring](https://link.springer.com/chapter/10.1007/978-3-030-81716-9_20) (2022)                                                                                                                                                                                                                                                                                                                                                                               |
+| 48 | Fuentes, Cross, Gardner, **Bull**, Rogers, Barthorpe, Shi, Dervilis, Farrar, Worden [Structural Health Monitoring and Damage Identification](https://link.springer.com/content/pdf/10.1007/978-1-4939-6503-8_23-1.pdf) (2020)                                                                                                                                                                                                                                                                                                                                       |
+| 64 | **Bull**, Abdallah, Mylonas, Avendaño-valencia, Tatsis, Gardner, Rogers, Brennan, Cross, Worden, Duncan, Dervilis, Girolami, Chatzi [Data-Centric Monitoring of Wind Farms: Combining Sources of Information](https://www.taylorfrancis.com/chapters/edit/10.1201/9781003306924-6/data-centric-monitoring-wind-farms-lawrence-bull-imad-abdallah-charilaos-mylonas-luis-david-avenda%C3%B1o-valencia-konstantinos-tatsis-paul-gardner-timothy-rogers-daniel-brennan-elizabeth-cross-keith-worden-andrew-duncan-nikolaos-dervilis-mark-girolami-eleni-chatzi) (None) |
 
@@
 |---:|:--------------------------------------------------------------------------------------------------------------------------------------|
-| 51 | **Bull** [Towards probabilistic and partially-supervised structural health monitoring](https://etheses.whiterose.ac.uk/26282/) (2019) |
+| 58 | **Bull** [Towards probabilistic and partially-supervised structural health monitoring](https://etheses.whiterose.ac.uk/26282/) (2019) |
 
 |    | Conference papers                                                                                                                                                                                                                                                                                                                                                                               |
-|---:|:---------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------|
-|  1 | Poole, Gardner, Dervilis, **Bull**, Worden [On the Application of Partial Domain Adaptation for PBSHM](https://link.springer.com/chapter/10.1007/978-3-031-07322-9_42) (2023)                                                                                                                                                                                              |
-|  2 | Dhada, **Bull**, Girolami, Parlikad [Modelling the Times-to-Failures Using a Statistical Hierarchical Model](https://link.springer.com/chapter/10.1007/978-3-031-07258-1_99) (2023)                                                                                                                                                                                        |
-| 12 | **Bull**, Dhada, Steinert, Lindgren, Parlikad, Girolami [Population-Level Modelling for Truck Fleet Survival Analysis](https://aspace.repository.cam.ac.uk/handle/1810/335452) (2022)                                                                                                                                                                                      |
-| 17 | Hughes, **Bull**, Gardner, Dervilis, Worden, Hughes [Semi-supervised risk-based active learning using inspection and maintenance information](https://eprints.whiterose.ac.uk/191598/) (2022)                                                                                                                                                                              |
-| 22 | Gardner, **Bull**, Dervilis, Worden [Challenges for SHM from Structural Repairs: An Outlier-Informed Domain Adaptation Approach](https://link.springer.com/chapter/10.1007/978-3-030-76004-5_10) (2022)                                                                                                                                                                    |
-| 23 | Gardner, **Bull**, Dervilis, Worden [On the Application of Heterogeneous Transfer Learning to Population-Based Structural Health Monitoring](https://link.springer.com/chapter/10.1007/978-3-030-76004-5_11) (2022)                                                                                                                                                        |
-| 24 | **Bull**, Gardner, Dervilis, Papatheou, Haywood-Alexander, Mills, Worden [Transferring Damage Detectors Between Tailplane Experiments](https://link.springer.com/chapter/10.1007/978-3-030-76004-5_22) (2022)                                                                                                                                                              |
-| 26 | Hughes, **Bull**, Gardner, Barthorpe, Dervilis, Worden [A risk-based active learning approach to inspection scheduling](https://www.researchgate.net/profile/Aidan-Hughes-4/publication/355903488_A_risk-based_active_learning_approach_to_inspection_scheduling/links/61892373d7d1af224bc69a96/A-risk-based-active-learning-approach-to-inspection-scheduling.pdf) (2021) |
-| 33 | **Bull**, Gardner, Dervilis, Papatheou, Worden [Automated Feature Extraction for Damage Detection: A Pseudo-fault Framework for Population-based SHM]() (2021)                                                                                                                                                                                                             |
-| 34 | **Bull**, Gardner, Dervilis, Worden [Normalising Flows and Nonlinear Normal Modes](https://www.sciencedirect.com/science/article/pii/S240589632101209X) (2021)                                                                                                                                                                                                             |
-| 35 | Gosliga, Gardner, **Bull**, Dervilis, Worden [Towards population-based structural health monitoring, Part III: Graphs, networks and communities](https://link.springer.com/chapter/10.1007/978-3-030-47717-2_26) (2021)                                                                                                                                                    |
-| 36 | Gosliga, Gardner, **Bull**, Dervilis, Worden [Towards population-based structural health monitoring, Part II: heterogeneous populations and structures as graphs](https://link.springer.com/chapter/10.1007/978-3-030-47717-2_17) (2021)                                                                                                                                   |
-| 39 | **Bull**, Gardner, Rogers, Cross, Dervilis, Worden [New Modes of Inference for Probabilistic SHM](https://link.springer.com/chapter/10.1007/978-3-030-64908-1_39) (2020)                                                                                                                                                                                                   |
-| 42 | Gardner, **Bull**, Gosliga, Dervilis, Worden [Towards population-based structural health monitoring, Part IV: heterogeneous populations, transfer and mapping](https://link.springer.com/chapter/10.1007/978-3-030-47638-0_20) (2020)                                                                                                                                      |
-| 43 | Gardner, **Bull**, Dervilis, Worden [Kernelised Bayesian transfer learning for population-based structural health monitoring](https://link.springer.com/chapter/10.1007/978-3-030-47638-0_22) (2020)                                                                                                                                                                       |
-| 44 | **Bull**, Gardner, Gosliga, Dervilis, Papatheou, Maguire, Campos, Rogers, Cross, Worden [Towards population-based structural health monitoring, Part I: Homogeneous populations and forms](https://link.springer.com/chapter/10.1007/978-3-030-47638-0_32) (2020)                                                                                                          |
-| 45 | **Bull**, Worden, Rogers, Cross, Dervilis [Investigating engineering data by probabilistic measures](https://link.springer.com/chapter/10.1007/978-3-030-12243-0_12) (2020)                                                                                                                                                                                                |
-| 48 | **Bull**, Worden, Rogers, Wickramarachchi, Cross, McLeay, Leahy, Dervilis [A probabilistic framework for online structural health monitoring: active learning from machining data streams](https://iopscience.iop.org/article/10.1088/1742-6596/1264/1/012028/meta) (2019)                                                                                                 |
-| 49 | **Bull**, Rogers, Dervilis, Cross, Worden [A Gaussian process form for population-based structural health monitoring](https://eprints.whiterose.ac.uk/148168/) (2019)                                                                                                                                                                                                      |
-| 50 | **Bull**, Dervilis, Worden [Experimental Validation of the Population-Form to Represent Nominally-Identical Systems](https://scholar.google.com/scholar?cluster=7507461710880003650&hl=en&oi=scholarr) (2019)                                                                                                                                                              |
-| 52 | **Bull**, Worden, Dervilis [Damage classification using labelled and unlabelled measurements](https://www.researchgate.net/profile/Lawrence-Bull-2/publication/337303717_Damage_Classification_Using_Labelled_and_Unlabelled_Measurements/links/62276fc93c53d31ba4b15c45/Damage-Classification-Using-Labelled-and-Unlabelled-Measurements.pdf) (2019)                      |
-| 53 | Dervilis, Zhang, **Bull**, Cross, Rogers, Fuentes, Dertimanis, Abdallah, Chatzi, Worden [A nonlinear robust outlier detection approach for SHM](https://eprints.whiterose.ac.uk/147321/) (2019)                                                                                                                                                                            |
-| 54 | **Bull**, Manson, Worden, Dervilis [Active Learning Approaches to Structural Health Monitoring](https://link.springer.com/chapter/10.1007/978-3-319-75390-4_14) (2019)                                                                                                                                                                                                     |
-| 56 | **Bull**, Worden, Cross, Dervilis [Outlier Ensembles: an Alternative Robust Method for Inclusive Outlier Analysis with Structural Health Monitoring Data]() (2018)                                                                                                                                                                                                         |
+|---:|:------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------|
+|  3 | Haywood-alexander, Worden, Dervilis, Mills, **Bull**, Dardeno [The Astir Glider Wing Dataset for Population-Based SHM](https://link.springer.com/chapter/10.1007/978-3-031-37007-6_3) (2023)                                                                                                                                                                                                    |
+| 16 | Poole, Gardner, Dervilis, **Bull**, Worden [On the application of partial domain adaptation for PBSHM](https://link.springer.com/chapter/10.1007/978-3-031-07322-9_42) (2022)                                                                                                                                                                                                                   |
+| 17 | Dhada, **Bull**, Girolami, Parlikad [Modelling the Times-to-Failures Using a Statistical Hierarchical Model](https://link.springer.com/chapter/10.1007/978-3-031-07258-1_99) (2022)                                                                                                                                                                                                             |
+| 20 | **Bull**, Dhada, Steinert, Lindgren, Parlikad, Girolami [Population-Level Modelling for Truck Fleet Survival Analysis](https://scholar.google.com/scholar?cluster=5740203727571381761&hl=en&oi=scholarr) (2022)                                                                                                                                                                                 |
+| 23 | Hughes, **Bull**, Gardner, Dervilis, Worden, Hughes [Semi-supervised risk-based active learning using inspection and maintenance information](https://eprints.whiterose.ac.uk/191598/) (2022)                                                                                                                                                                                                   |
+| 26 | Gardner, **Bull**, Dervilis, Worden [Challenges for SHM from Structural Repairs: An Outlier-Informed Domain Adaptation Approach](https://link.springer.com/chapter/10.1007/978-3-030-76004-5_10) (2022)                                                                                                                                                                                         |
+| 27 | Gardner, **Bull**, Dervilis, Worden [On the Application of Heterogeneous Transfer Learning to Population-Based Structural Health Monitoring](https://link.springer.com/chapter/10.1007/978-3-030-76004-5_11) (2022)                                                                                                                                                                             |
+| 28 | **Bull**, Gardner, Dervilis, Papatheou, Haywood-alexander, Mills, Worden [Transferring Damage Detectors Between Tailplane Experiments](https://link.springer.com/chapter/10.1007/978-3-030-76004-5_22) (2022)                                                                                                                                                                                   |
+| 30 | Hughes, **Bull**, Gardner, Barthorpe, Dervilis, Worden [A risk-based active learning approach to inspection scheduling](https://www.researchgate.net/profile/Aidan-Hughes-4/publication/355903488_A_risk-based_active_learning_approach_to_inspection_scheduling/links/61892373d7d1af224bc69a96/A-risk-based-active-learning-approach-to-inspection-scheduling.pdf) (2021)                      |
+| 40 | **Bull**, Gardner, Dervilis, Papatheou, Worden [Automated Feature Extraction for Damage Detection: A Pseudo-fault Framework for Population-based SHM]() (2021)                                                                                                                                                                                                                                  |
+| 41 | **Bull**, Gardner, Dervilis, Worden [Normalising Flows and Nonlinear Normal Modes](https://www.sciencedirect.com/science/article/pii/S240589632101209X) (2021)                                                                                                                                                                                                                                  |
+| 42 | Gosliga, Gardner, **Bull**, Dervilis, Worden [Towards population-based structural health monitoring, Part III: Graphs, networks and communities](https://link.springer.com/chapter/10.1007/978-3-030-47717-2_26) (2021)                                                                                                                                                                         |
+| 43 | Gosliga, Gardner, **Bull**, Dervilis, Worden [Towards population-based structural health monitoring, Part II: heterogeneous populations and structures as graphs](https://link.springer.com/chapter/10.1007/978-3-030-47717-2_17) (2021)                                                                                                                                                        |
+| 46 | **Bull**, Gardner, Rogers, Cross, Dervilis, Worden [New Modes of Inference for Probabilistic SHM](https://link.springer.com/chapter/10.1007/978-3-030-64908-1_39) (2020)                                                                                                                                                                                                                        |
+| 49 | Gardner, **Bull**, Gosliga, Dervilis, Worden [Towards population-based structural health monitoring, Part IV: heterogeneous populations, transfer and mapping](https://link.springer.com/chapter/10.1007/978-3-030-47638-0_20) (2020)                                                                                                                                                           |
+| 50 | Gardner, **Bull**, Dervilis, Worden [Kernelised Bayesian transfer learning for population-based structural health monitoring](https://link.springer.com/chapter/10.1007/978-3-030-47638-0_22) (2020)                                                                                                                                                                                            |
+| 51 | **Bull**, Gardner, Gosliga, Dervilis, Papatheou, Maguire, Campos, Rogers, Cross, Worden [Towards population-based structural health monitoring, Part I: Homogeneous populations and forms](https://link.springer.com/chapter/10.1007/978-3-030-47638-0_32) (2020)                                                                                                                               |
+| 52 | **Bull**, Worden, Rogers, Cross, Dervilis [Investigating engineering data by probabilistic measures](https://link.springer.com/chapter/10.1007/978-3-030-12243-0_12) (2020)                                                                                                                                                                                                                     |
+| 55 | **Bull**, Worden, Rogers, Wickramarachchi, Cross, Mcleay, Leahy, Dervilis [A probabilistic framework for online structural health monitoring: active learning from machining data streams](https://iopscience.iop.org/article/10.1088/1742-6596/1264/1/012028/meta) (2019)                                                                                                                      |
+| 56 | **Bull**, Rogers, Dervilis, Cross, Worden [A Gaussian process form for population-based structural health monitoring](https://www.researchgate.net/profile/Lawrence-Bull-2/publication/334250549_A_Gaussian_process_form_for_population-based_structural_health_monitoring/links/622771023c53d31ba4b15c72/A-Gaussian-process-form-for-population-based-structural-health-monitoring.pdf) (2019) |
+| 57 | **Bull**, Dervilis, Worden [Experimental Validation of the Population-Form to Represent Nominally-Identical Systems](https://www.dpi-proceedings.com/index.php/shm2019/article/view/32373) (2019)                                                                                                                                                                                               |
+| 59 | **Bull**, Worden, Dervilis [Damage classification using labelled and unlabelled measurements](https://www.researchgate.net/profile/Lawrence-Bull-2/publication/337303717_Damage_Classification_Using_Labelled_and_Unlabelled_Measurements/links/62276fc93c53d31ba4b15c45/Damage-Classification-Using-Labelled-and-Unlabelled-Measurements.pdf) (2019)                                           |
+| 60 | Dervilis, Zhang, **Bull**, Cross, Rogers, Fuentes, Dertimanis, Abdallah, Chatzi, Worden [A nonlinear robust outlier detection approach for SHM](https://eprints.whiterose.ac.uk/147321/) (2019)                                                                                                                                                                                                 |
+| 61 | **Bull**, Manson, Worden, Dervilis [Active Learning Approaches to Structural Health Monitoring](https://link.springer.com/chapter/10.1007/978-3-319-75390-4_14) (2019)                                                                                                                                                                                                                          |
+| 63 | **Bull**, Worden, Cross, Dervilis [Outlier Ensembles: an Alternative Robust Method for Inclusive Outlier Analysis with Structural Health Monitoring Data]() (2018)                                                                                                                                                                                                                              |
 

### 2024-04-02 index.qmd
glasgow

@@
 [wind turbines](https://arxiv.org/abs/2111.15496)).
-By encoding domain expertise into statistical models, complex representations can be built from interpretable units, allowing machines to share information and increase the value of data.
+By encoding domain expertise into statistical models, complex representations can be built from interpretable units, allowing machines to share information and increasing the value of data.
 <!-- At a systems level, alternative insights can emerge that might otherwise be missed -- the whole is something _besides_ its parts. -->

### 2024-04-24 papers.qmd
pubs update

--- 2023-01-15 papers.qmd
@@
 |---:|:------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------|
-|  3 | **Bull**, Dhada, Steinert, Lindgren, Parlikad, Duncan, Girolami [Knowledge Transfer in Engineering Fleets: Hierarchical Bayesian Modelling for Multi-Task Learning](https://arxiv.org/abs/2204.12404) (2022)                                                                              |
-|  4 | **Bull**, Dervilis, Worden, Cross, Rogers [A sampling-based approach for information-theoretic inspection management](https://royalsocietypublishing.org/doi/abs/10.1098/rspa.2021.0790) (2022)                                                                                           |
-|  8 | Gardner, **Bull**, Gosliga, Poole, Dervilis, Worden [A population-based SHM methodology for heterogeneous structures: Transferring damage localisation knowledge between different aircraft wings](https://www.sciencedirect.com/science/article/pii/S0888327022001030) (2022)            |
-| 10 | **Bull**, Gardner, Rogers, Dervilis, Cross, Papatheou, Maguire, Campos, Worden [Bayesian modelling of multivalued power curves from an operational wind farm](https://www.sciencedirect.com/science/article/pii/S0888327021008724) (2022)                                                 |
-| 11 | Gardner, **Bull**, Dervilis, Worden [Domain-adapted Gaussian mixture models for population-based structural health monitoring](https://link.springer.com/article/10.1007/s13349-022-00565-5) (2022)                                                                                       |
-| 13 | Gardner, **Bull**, Dervilis, Worden [On the application of kernelised Bayesian transfer learning to population-based structural health monitoring](https://www.sciencedirect.com/science/article/pii/S088832702100861X) (2022)                                                            |
-| 14 | Hughes, **Bull**, Gardner, Barthorpe, Dervilis, Worden [On risk-based active learning for structural health monitoring](https://www.sciencedirect.com/science/article/pii/S0888327021009055) (2022)                                                                                       |
-| 18 | Dardeno, Haywood-Alexander, Mills, **Bull**, Dervilis, Worden [Investigating the effects of ambient temperature on feature consistency in vibration-based SHM](https://scholar.google.com/scholar?cluster=624769372939145628&hl=en&oi=scholarr) (2022)                                    |
-| 19 | Dardeno, **Bull**, Dervilis, Worden [Investigating experimental repeatability and feature consistency in vibration-based SHM](https://scholar.google.com/scholar?cluster=10140930682997029543&hl=en&oi=scholarr) (2022)                                                                   |
-| 25 | Gardner, **Bull**, Dervilis, Worden [Overcoming the problem of repair in structural health monitoring: Metric-informed transfer learning](https://www.sciencedirect.com/science/article/pii/S0022460X21003175) (2021)                                                                     |
-| 27 | **Bull**, Gardner, Dervilis, Papatheou, Haywood-Alexander, Mills, Worden [On the transfer of damage detectors between structures: an experimental case study](https://www.sciencedirect.com/science/article/pii/S0022460X21001449) (2021)                                                 |
-| 28 | **Bull**, Gardner, Rogers, Cross, Dervilis, Worden [Probabilistic inference for structural health monitoring: new modes of learning from data](https://ascelibrary.org/doi/abs/10.1061/AJRUA6.0001106) (2021)                                                                             |
-| 29 | Gardner, **Bull**, Gosliga, Dervilis, Worden [Foundations of population-based SHM, Part III: Heterogeneous populations–Mapping and transfer](https://www.sciencedirect.com/science/article/pii/S0888327020305288) (2021)                                                                  |
-| 30 | **Bull**, Gardner, Gosliga, Rogers, Dervilis, Cross, Papatheou, Maguire, Campos, Worden [Foundations of population-based SHM, Part I: Homogeneous populations and forms](https://www.sciencedirect.com/science/article/pii/S0888327020305276) (2021)                                      |
-| 31 | Gosliga, Gardner, **Bull**, Dervilis, Worden [Foundations of Population-based SHM, Part II: Heterogeneous populations–Graphs, networks, and communities](https://www.sciencedirect.com/science/article/pii/S0888327020305306) (2021)                                                      |
-| 32 | Poole, Gardner, Dervilis, **Bull**, Worden [On normalisation for domain adaptation in population-based structural health monitoring](https://scholar.google.com/scholar?cluster=9278611934387106844&hl=en&oi=scholarr) (2021)                                                             |
-| 37 | Zammit, **Bull**, Sanders, Galvin, Dervilis, Sidhu, Worden [Towards the Probabilistic Analysis of Small Bowel Capsule Endoscopy Features to Predict Severity of Duodenal Histology in Patients with Villous Atrophy](https://link.springer.com/article/10.1007/s10916-020-01657-9) (2020) |
-| 38 | Worden, **Bull**, Gardner, Gosliga, Rogers, Cross, Papatheou, Lin, Dervilis [A brief introduction to recent developments in population-based structural health monitoring](https://www.frontiersin.org/articles/10.3389/fbuil.2020.00146/full) (2020)                                     |
-| 40 | **Bull**, Worden, Dervilis [Towards semi-supervised and probabilistic classification in structural health monitoring](https://www.sciencedirect.com/science/article/pii/S088832702030039X) (2020)                                                                                         |
-| 46 | **Bull**, Rogers, Wickramarachchi, Cross, Worden, Dervilis [Probabilistic active learning: an online framework for structural health monitoring](https://www.sciencedirect.com/science/article/pii/S0888327019305096) (2019)                                                              |
-| 47 | **Bull**, Worden, Fuentes, Manson, Cross, Dervilis [Outlier ensembles: A robust method for damage detection and unsupervised feature extraction from high-dimensional data](https://www.sciencedirect.com/science/article/pii/S0022460X1930197X) (2019)                                   |
-| 55 | **Bull**, Worden, Manson, Dervilis [Active learning for semi-supervised structural health monitoring](https://www.sciencedirect.com/science/article/pii/S0022460X18305479) (2018)                                                                                                         |
+|  3 | Dardeno, Worden, Dervilis, Mills, **Bull** [On the hierarchical Bayesian modelling of frequency response functions](https://www.sciencedirect.com/science/article/pii/S0888327023009809) (2024)                                                                                           |
+|  4 | Bee, Poole, Worden, Dervilis, **Bull** [Multitask feature selection within structural datasets](https://www.cambridge.org/core/journals/data-centric-engineering/article/multitask-feature-selection-within-structural-datasets/FC9171AF330232B4B07955F807C5BBD4) (2024)                  |
+| 12 | Poole, Gardner, Dervilis, **Bull**, Worden [On statistic alignment for domain adaptation in structural health monitoring](https://journals.sagepub.com/doi/abs/10.1177/14759217221110441) (2023)                                                                                          |
+| 13 | Dardeno, **Bull**, Mills, Dervilis, Worden [Hierarchical Bayesian Modelling of a Family of FRFs](https://scholar.google.com/scholar?cluster=12496156724459680049&hl=en&oi=scholarr) (2023)                                                                                                |
+| 14 | Gardner, **Bull**, Dervilis, Worden [Domain-adapted Gaussian mixture models for population-based structural health monitoring](https://link.springer.com/article/10.1007/s13349-022-00565-5) (2022)                                                                                       |
+| 15 | Hughes, **Bull**, Gardner, Dervilis, Worden [On robust risk-based active-learning algorithms for enhanced decision support](https://www.sciencedirect.com/science/article/pii/S0888327022006124) (2022)                                                                                   |
+| 16 | Dardeno, **Bull**, Mills, Dervilis, Worden [Modelling variability in vibration-based PBSHM via a generalised population form](https://www.sciencedirect.com/science/article/pii/S0022460X22004151) (2022)                                                                                 |
+| 17 | **Bull**, Dhada, Steinert, Lindgren, Parlikad, Duncan, Girolami [Knowledge Transfer in Engineering Fleets: Hierarchical Bayesian Modelling for Multi-Task Learning](https://scholar.google.com/scholar?cluster=9172883967640918731&hl=en&oi=scholarr) (2022)                              |
+| 18 | **Bull**, Dervilis, Worden, Cross, Rogers [A sampling-based approach for information-theoretic inspection management](https://royalsocietypublishing.org/doi/abs/10.1098/rspa.2021.0790) (2022)                                                                                           |
+| 24 | Gardner, **Bull**, Gosliga, Poole, Dervilis, Worden [A population-based SHM methodology for heterogeneous structures: Transferring damage localisation knowledge between different aircraft wings](https://www.sciencedirect.com/science/article/pii/S0888327022001030) (2022)            |
+| 25 | **Bull**, Gardner, Rogers, Dervilis, Cross, Papatheou, Maguire, Campos, Worden [Bayesian modelling of multivalued power curves from an operational wind farm](https://www.sciencedirect.com/science/article/pii/S0888327021008724) (2022)                                                 |
+| 27 | Gardner, **Bull**, Dervilis, Worden [On the application of kernelised Bayesian transfer learning to population-based structural health monitoring](https://www.sciencedirect.com/science/article/pii/S088832702100861X) (2022)                                                            |
+| 28 | Hughes, **Bull**, Gardner, Barthorpe, Dervilis, Worden [On risk-based active learning for structural health monitoring](https://www.sciencedirect.com/science/article/pii/S0888327021009055) (2022)                                                                                       |
+| 35 | Gardner, **Bull**, Dervilis, Worden [Overcoming the problem of repair in structural health monitoring: Metric-informed transfer learning](https://www.sciencedirect.com/science/article/pii/S0022460X21003175) (2021)                                                                     |
+| 37 | **Bull**, Gardner, Dervilis, Papatheou, Haywood-alexander, Mills, Worden [On the transfer of damage detectors between structures: An experimental case study](https://www.sciencedirect.com/science/article/pii/S0022460X21001449) (2021)                                                 |
+| 38 | **Bull**, Gardner, Rogers, Cross, Dervilis, Worden [Probabilistic inference for structural health monitoring: new modes of learning from data](https://ascelibrary.org/doi/abs/10.1061/AJRUA6.0001106) (2021)                                                                             |
+| 39 | Gardner, **Bull**, Gosliga, Dervilis, Worden [Foundations of population-based SHM, Part III: Heterogeneous populations–Mapping and transfer](https://www.sciencedirect.com/science/article/pii/S0888327020305288) (2021)                                                                  |
+| 40 | **Bull**, Gardner, Gosliga, Rogers, Dervilis, Cross, Papatheou, Maguire, Campos, Worden [Foundations of population-based SHM, Part I: Homogeneous populations and forms](https://www.sciencedirect.com/science/article/pii/S0888327020305276) (2021)                                      |
+| 41 | Gosliga, Gardner, **Bull**, Dervilis, Worden [Foundations of Population-based SHM, Part II: Heterogeneous populations–Graphs, networks, and communities](https://www.sciencedirect.com/science/article/pii/S0888327020305306) (2021)                                                      |
+| 42 | Gardner, **Bull**, Gosliga, Poole, Dervilis, Worden [On a Population-Based Structural Health Monitoring Framework: An Aerospace Case Study](https://scholar.google.com/scholar?cluster=4043708261387081096&hl=en&oi=scholarr) (2021)                                                      |
+| 43 | Dardeno, Haywood-alexander, Mills, **Bull**, Dervilis, Worden [Investigating the effects of ambient temperature on feature consistency in vibration-based SHM](https://scholar.google.com/scholar?cluster=9923012878070308352&hl=en&oi=scholarr) (2021)                                   |
+| 44 | Dardeno, **Bull**, Dervilis, Worden [Investigating experimental repeatability and feature consistency in vibration-based SHM](https://scholar.google.com/scholar?cluster=310368606763056725&hl=en&oi=scholarr) (2021)                                                                     |
+| 45 | Poole, Gardner, Dervilis, **Bull**, Worden [On normalisation for domain adaptation in population-based structural health monitoring](https://scholar.google.com/scholar?cluster=9278611934387106844&hl=en&oi=scholarr) (2021)                                                             |
+| 50 | Zammit, **Bull**, Sanders, Galvin, Dervilis, Sidhu, Worden [Towards the Probabilistic Analysis of Small Bowel Capsule Endoscopy Features to Predict Severity of Duodenal Histology in Patients with Villous Atrophy](https://link.springer.com/article/10.1007/s10916-020-01657-9) (2020) |
+| 51 | Worden, **Bull**, Gardner, Gosliga, Rogers, Cross, Papatheou, Lin, Dervilis [A brief introduction to recent developments in population-based structural health monitoring](https://www.frontiersin.org/articles/10.3389/fbuil.2020.00146/full) (2020)                                     |
+| 53 | **Bull**, Worden, Dervilis [Towards semi-supervised and probabilistic classification in structural health monitoring](https://www.sciencedirect.com/science/article/pii/S088832702030039X) (2020)                                                                                         |
+| 59 | **Bull**, Rogers, Wickramarachchi, Cross, Worden, Dervilis [Probabilistic active learning: an online framework for structural health monitoring](https://www.sciencedirect.com/science/article/pii/S0888327019305096) (2019)                                                              |
+| 60 | **Bull**, Worden, Fuentes, Manson, Cross, Dervilis [Outlier ensembles: A robust method for damage detection and unsupervised feature extraction from high-dimensional data](https://www.sciencedirect.com/science/article/pii/S0022460X1930197X) (2019)                                   |
+| 68 | **Bull**, Worden, Manson, Dervilis [Active learning for semi-supervised structural health monitoring](https://www.sciencedirect.com/science/article/pii/S0022460X18305479) (2018)                                                                                                         |
 
 |    | Preprints                                                                                                                                                                                                        |
-|---:|:------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------|
-|  5 | Hughes, **Bull**, Gardner, Dervilis, Worden [Mitigating sampling bias in risk-based active learning via an EM algorithm](https://arxiv.org/abs/2206.12598) (2022)                               |
-|  6 | Dardeno, **Bull**, Dervilis, Worden [A generalised form for a homogeneous population of structures using an overlapping mixture of Gaussian processes](https://arxiv.org/abs/2206.11683) (2022) |
-|  7 | Hughes, Gardner, **Bull**, Dervilis, Worden [Improving decision-making via risk-based active learning: Probabilistic discriminative classifiers](https://arxiv.org/abs/2206.11616) (2022)       |
-|  9 | Poole, Gardner, Dervilis, **Bull**, Worden [On statistic alignment for domain adaptation in structural health monitoring](https://arxiv.org/abs/2205.12052) (2022)                              |
-| 15 | Dardeno, **Bull**, Mills, Dervilis, Worden [Modelling variability in vibration-based PBSHM via a generalised population form](https://arxiv.org/abs/2203.07115) (2022)                          |
-| 16 | Hughes, **Bull**, Gardner, Dervilis, Worden [On robust risk-based active-learning algorithms for enhanced decision support](https://arxiv.org/abs/2201.02555) (2022)                            |
+|---:|:-----------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------|
+|  1 | **Bull**, Jeon, Girolami, Duncan, Schooling, Haro [Towards Multilevel Modelling of Train Passing Events on the Staffordshire Bridge](https://arxiv.org/abs/2403.17820) (2024)                                    |
+|  2 | Smith, Hughes, Dardeno, **Bull**, Dervilis, Worden [Anomaly Detection in Offshore Wind Turbine Structures using Hierarchical Bayesian Modelling](https://arxiv.org/abs/2402.19295) (2024)                        |
+|  6 | Clarkson, **Bull**, Dardeno, Wickramarachchi, Cross, Rogers, Worden, Dervilis, Hughes [Sharing Information Between Machine Tools to Improve Surface Finish Forecasting](https://arxiv.org/abs/2310.05807) (2023) |
+| 10 | Bee, **Bull**, Dervilis, Worden [When is an SHM problem a Multi-Task-Learning problem?](https://arxiv.org/abs/2305.09425) (2023)                                                                                 |
+| 11 | **Bull**, Jones, Cross, Duncan, Girolami [Encoding domain expertise into multilevel models for source location](https://arxiv.org/abs/2305.08657) (2023)                                                         |
+| 19 | Hughes, **Bull**, Gardner, Dervilis, Worden [Mitigating sampling bias in risk-based active learning via an EM algorithm](https://arxiv.org/abs/2206.12598) (2022)                                                |
+| 20 | Dardeno, **Bull**, Dervilis, Worden [A generalised form for a homogeneous population of structures using an overlapping mixture of Gaussian processes](https://arxiv.org/abs/2206.11683) (2022)                  |
+| 21 | Hughes, Gardner, **Bull**, Dervilis, Worden [Improving decision-making via risk-based active learning: Probabilistic discriminative classifiers](https://arxiv.org/abs/2206.11616) (2022)                        |
 
 |    | Book chapters                                                                                                                                                                                                                                                                                                                                       |
-|---:|:------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------|
-| 20 | **Bull**, Hughes, Rogers, Gardner, Worden, Dervilis [Partially Supervised Learning for Data-Driven Structural Health Monitoring](https://link.springer.com/chapter/10.1007/978-3-030-81716-9_19) (2022)                       |
-| 21 | Gardner, **Bull**, Gosliga, Dervilis, Cross, Papatheou, Worden [Population-Based Structural Health Monitoring](https://link.springer.com/chapter/10.1007/978-3-030-81716-9_20) (2022)                                         |
-| 41 | Fuentes, Cross, Gardner, **Bull**, Rogers, Barthorpe, Shi, Dervilis, Farrar, Worden [Structural Health Monitoring and Damage Identification](https://link.springer.com/content/pdf/10.1007/978-1-4939-6503-8_23-1.pdf) (2020) |
+|---:|:----------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------|
+|  5 | **Bull**, Abdallah, Mylonas, Avendaño-valencia, Tatsis, Gardner, Rogers, Brennan, Cross, Worden, Duncan, Dervilis, Girolami, Chatzi [Data-Centric Monitoring of Wind Farms](https://books.google.com/books?hl=en&lr=&id=x57WEAAAQBAJ&oi=fnd&pg=PA206&dq=info:opW30yPHEQIJ:scholar.google.com&ots=4hHqzfiRFx&sig=T4IA_LQs95P5BNQY_n1Qk7m4lxs) (2023) |
+| 30 | **Bull**, Hughes, Rogers, Gardner, Worden, Dervilis [Partially Supervised Learning for Data-Driven Structural Health Monitoring](https://link.springer.com/chapter/10.1007/978-3-030-81716-9_19) (2022)                                                                                                                                             |
+| 31 | Gardner, **Bull**, Gosliga, Dervilis, Cross, Papatheou, Worden [Population-Based Structural Health Monitoring](https://link.springer.com/chapter/10.1007/978-3-030-81716-9_20) (2022)                                                                                                                                                               |
+| 54 | Fuentes, Cross, Gardner, **Bull**, Rogers, Barthorpe, Shi, Dervilis, Farrar, Worden [Structural Health Monitoring and Damage Identification](https://link.springer.com/content/pdf/10.1007/978-1-4939-6503-8_23-1.pdf) (2020)                                                                                                                       |
 
@@
 |---:|:--------------------------------------------------------------------------------------------------------------------------------------|
-| 51 | **Bull** [Towards probabilistic and partially-supervised structural health monitoring](https://etheses.whiterose.ac.uk/26282/) (2019) |
+| 64 | **Bull** [Towards probabilistic and partially-supervised structural health monitoring](https://etheses.whiterose.ac.uk/26282/) (2019) |
 
 |    | Conference papers                                                                                                                                                                                                                                                                                                                                                                               |
-|---:|:---------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------|
-|  1 | Poole, Gardner, Dervilis, **Bull**, Worden [On the Application of Partial Domain Adaptation for PBSHM](https://link.springer.com/chapter/10.1007/978-3-031-07322-9_42) (2023)                                                                                                                                                                                              |
-|  2 | Dhada, **Bull**, Girolami, Parlikad [Modelling the Times-to-Failures Using a Statistical Hierarchical Model](https://link.springer.com/chapter/10.1007/978-3-031-07258-1_99) (2023)                                                                                                                                                                                        |
-| 12 | **Bull**, Dhada, Steinert, Lindgren, Parlikad, Girolami [Population-Level Modelling for Truck Fleet Survival Analysis](https://aspace.repository.cam.ac.uk/handle/1810/335452) (2022)                                                                                                                                                                                      |
-| 17 | Hughes, **Bull**, Gardner, Dervilis, Worden, Hughes [Semi-supervised risk-based active learning using inspection and maintenance information](https://eprints.whiterose.ac.uk/191598/) (2022)                                                                                                                                                                              |
-| 22 | Gardner, **Bull**, Dervilis, Worden [Challenges for SHM from Structural Repairs: An Outlier-Informed Domain Adaptation Approach](https://link.springer.com/chapter/10.1007/978-3-030-76004-5_10) (2022)                                                                                                                                                                    |
-| 23 | Gardner, **Bull**, Dervilis, Worden [On the Application of Heterogeneous Transfer Learning to Population-Based Structural Health Monitoring](https://link.springer.com/chapter/10.1007/978-3-030-76004-5_11) (2022)                                                                                                                                                        |
-| 24 | **Bull**, Gardner, Dervilis, Papatheou, Haywood-Alexander, Mills, Worden [Transferring Damage Detectors Between Tailplane Experiments](https://link.springer.com/chapter/10.1007/978-3-030-76004-5_22) (2022)                                                                                                                                                              |
-| 26 | Hughes, **Bull**, Gardner, Barthorpe, Dervilis, Worden [A risk-based active learning approach to inspection scheduling](https://www.researchgate.net/profile/Aidan-Hughes-4/publication/355903488_A_risk-based_active_learning_approach_to_inspection_scheduling/links/61892373d7d1af224bc69a96/A-risk-based-active-learning-approach-to-inspection-scheduling.pdf) (2021) |
-| 33 | **Bull**, Gardner, Dervilis, Papatheou, Worden [Automated Feature Extraction for Damage Detection: A Pseudo-fault Framework for Population-based SHM]() (2021)                                                                                                                                                                                                             |
-| 34 | **Bull**, Gardner, Dervilis, Worden [Normalising Flows and Nonlinear Normal Modes](https://www.sciencedirect.com/science/article/pii/S240589632101209X) (2021)                                                                                                                                                                                                             |
-| 35 | Gosliga, Gardner, **Bull**, Dervilis, Worden [Towards population-based structural health monitoring, Part III: Graphs, networks and communities](https://link.springer.com/chapter/10.1007/978-3-030-47717-2_26) (2021)                                                                                                                                                    |
-| 36 | Gosliga, Gardner, **Bull**, Dervilis, Worden [Towards population-based structural health monitoring, Part II: heterogeneous populations and structures as graphs](https://link.springer.com/chapter/10.1007/978-3-030-47717-2_17) (2021)                                                                                                                                   |
-| 39 | **Bull**, Gardner, Rogers, Cross, Dervilis, Worden [New Modes of Inference for Probabilistic SHM](https://link.springer.com/chapter/10.1007/978-3-030-64908-1_39) (2020)                                                                                                                                                                                                   |
-| 42 | Gardner, **Bull**, Gosliga, Dervilis, Worden [Towards population-based structural health monitoring, Part IV: heterogeneous populations, transfer and mapping](https://link.springer.com/chapter/10.1007/978-3-030-47638-0_20) (2020)                                                                                                                                      |
-| 43 | Gardner, **Bull**, Dervilis, Worden [Kernelised Bayesian transfer learning for population-based structural health monitoring](https://link.springer.com/chapter/10.1007/978-3-030-47638-0_22) (2020)                                                                                                                                                                       |
-| 44 | **Bull**, Gardner, Gosliga, Dervilis, Papatheou, Maguire, Campos, Rogers, Cross, Worden [Towards population-based structural health monitoring, Part I: Homogeneous populations and forms](https://link.springer.com/chapter/10.1007/978-3-030-47638-0_32) (2020)                                                                                                          |
-| 45 | **Bull**, Worden, Rogers, Cross, Dervilis [Investigating engineering data by probabilistic measures](https://link.springer.com/chapter/10.1007/978-3-030-12243-0_12) (2020)                                                                                                                                                                                                |
-| 48 | **Bull**, Worden, Rogers, Wickramarachchi, Cross, McLeay, Leahy, Dervilis [A probabilistic framework for online structural health monitoring: active learning from machining data streams](https://iopscience.iop.org/article/10.1088/1742-6596/1264/1/012028/meta) (2019)                                                                                                 |
-| 49 | **Bull**, Rogers, Dervilis, Cross, Worden [A Gaussian process form for population-based structural health monitoring](https://eprints.whiterose.ac.uk/148168/) (2019)                                                                                                                                                                                                      |
-| 50 | **Bull**, Dervilis, Worden [Experimental Validation of the Population-Form to Represent Nominally-Identical Systems](https://scholar.google.com/scholar?cluster=7507461710880003650&hl=en&oi=scholarr) (2019)                                                                                                                                                              |
-| 52 | **Bull**, Worden, Dervilis [Damage classification using labelled and unlabelled measurements](https://www.researchgate.net/profile/Lawrence-Bull-2/publication/337303717_Damage_Classification_Using_Labelled_and_Unlabelled_Measurements/links/62276fc93c53d31ba4b15c45/Damage-Classification-Using-Labelled-and-Unlabelled-Measurements.pdf) (2019)                      |
-| 53 | Dervilis, Zhang, **Bull**, Cross, Rogers, Fuentes, Dertimanis, Abdallah, Chatzi, Worden [A nonlinear robust outlier detection approach for SHM](https://eprints.whiterose.ac.uk/147321/) (2019)                                                                                                                                                                            |
-| 54 | **Bull**, Manson, Worden, Dervilis [Active Learning Approaches to Structural Health Monitoring](https://link.springer.com/chapter/10.1007/978-3-319-75390-4_14) (2019)                                                                                                                                                                                                     |
-| 56 | **Bull**, Worden, Cross, Dervilis [Outlier Ensembles: an Alternative Robust Method for Inclusive Outlier Analysis with Structural Health Monitoring Data]() (2018)                                                                                                                                                                                                         |
+|---:|:------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------|
+|  7 | Dardeno, **Bull**, Dervilis, Worden [A population form via hierarchical Bayesian modelling of the FRF](https://link.springer.com/chapter/10.1007/978-3-031-34946-1_11) (2023)                                                                                                                                                                                                                   |
+|  8 | Haywood-alexander, Worden, Dervilis, Mills, **Bull**, Dardeno [The Astir Glider Wing Dataset for Population-Based SHM](https://link.springer.com/chapter/10.1007/978-3-031-37007-6_3) (2023)                                                                                                                                                                                                    |
+|  9 | Bee, Papatheou, Haywood-alexander, Mills, **Bull**, Worden, Dervilis [Better Together: Using Multi-Task Learning to Improve Feature Selection Within Structural Datasets](https://link.springer.com/chapter/10.1007/978-3-031-34946-1_7) (2023)                                                                                                                                                 |
+| 22 | Poole, Gardner, Dervilis, **Bull**, Worden [On the application of partial domain adaptation for pbshm](https://link.springer.com/chapter/10.1007/978-3-031-07322-9_42) (2022)                                                                                                                                                                                                                   |
+| 23 | Dhada, **Bull**, Girolami, Parlikad [Modelling the Times-to-Failures Using a Statistical Hierarchical Model](https://link.springer.com/chapter/10.1007/978-3-031-07258-1_99) (2022)                                                                                                                                                                                                             |
+| 26 | **Bull**, Dhada, Steinert, Lindgren, Parlikad, Girolami [Population-Level Modelling for Truck Fleet Survival Analysis](https://www.repository.cam.ac.uk/items/f7d7fc3d-a2bd-412d-b7da-e5c5e40c1392) (2022)                                                                                                                                                                                      |
+| 29 | Hughes, **Bull**, Gardner, Dervilis, Worden, Hughes [Semi-supervised risk-based active learning using inspection and maintenance information](https://eprints.whiterose.ac.uk/191598/) (2022)                                                                                                                                                                                                   |
+| 32 | Gardner, **Bull**, Dervilis, Worden [Challenges for SHM from Structural Repairs: An Outlier-Informed Domain Adaptation Approach](https://link.springer.com/chapter/10.1007/978-3-030-76004-5_10) (2022)                                                                                                                                                                                         |
+| 33 | Gardner, **Bull**, Dervilis, Worden [On the Application of Heterogeneous Transfer Learning to Population-Based Structural Health Monitoring](https://link.springer.com/chapter/10.1007/978-3-030-76004-5_11) (2022)                                                                                                                                                                             |
+| 34 | **Bull**, Gardner, Dervilis, Papatheou, Haywood-alexander, Mills, Worden [Transferring Damage Detectors Between Tailplane Experiments](https://link.springer.com/chapter/10.1007/978-3-030-76004-5_22) (2022)                                                                                                                                                                                   |
+| 36 | Hughes, **Bull**, Gardner, Barthorpe, Dervilis, Worden [A risk-based active learning approach to inspection scheduling](https://www.researchgate.net/profile/Aidan-Hughes-4/publication/355903488_A_risk-based_active_learning_approach_to_inspection_scheduling/links/61892373d7d1af224bc69a96/A-risk-based-active-learning-approach-to-inspection-scheduling.pdf) (2021)                      |
+| 46 | **Bull**, Gardner, Dervilis, Papatheou, Worden [Automated Feature Extraction for Damage Detection: A Pseudo-fault Framework for Population-based SHM]() (2021)                                                                                                                                                                                                                                  |
+| 47 | **Bull**, Gardner, Dervilis, Worden [Normalising Flows and Nonlinear Normal Modes](https://www.sciencedirect.com/science/article/pii/S240589632101209X) (2021)                                                                                                                                                                                                                                  |
+| 48 | Gosliga, Gardner, **Bull**, Dervilis, Worden [Towards population-based structural health monitoring, Part III: Graphs, networks and communities](https://link.springer.com/chapter/10.1007/978-3-030-47717-2_26) (2021)                                                                                                                                                                         |
+| 49 | Gosliga, Gardner, **Bull**, Dervilis, Worden [Towards population-based structural health monitoring, Part II: heterogeneous populations and structures as graphs](https://link.springer.com/chapter/10.1007/978-3-030-47717-2_17) (2021)                                                                                                                                                        |
+| 52 | **Bull**, Gardner, Rogers, Cross, Dervilis, Worden [New Modes of Inference for Probabilistic SHM](https://link.springer.com/chapter/10.1007/978-3-030-64908-1_39) (2020)                                                                                                                                                                                                                        |
+| 55 | Gardner, **Bull**, Gosliga, Dervilis, Worden [Towards population-based structural health monitoring, Part IV: heterogeneous populations, transfer and mapping](https://link.springer.com/chapter/10.1007/978-3-030-47638-0_20) (2020)                                                                                                                                                           |
+| 56 | Gardner, **Bull**, Dervilis, Worden [Kernelised Bayesian transfer learning for population-based structural health monitoring](https://link.springer.com/chapter/10.1007/978-3-030-47638-0_22) (2020)                                                                                                                                                                                            |
+| 57 | **Bull**, Gardner, Gosliga, Dervilis, Papatheou, Maguire, Campos, Rogers, Cross, Worden [Towards population-based structural health monitoring, Part I: Homogeneous populations and forms](https://link.springer.com/chapter/10.1007/978-3-030-47638-0_32) (2020)                                                                                                                               |
+| 58 | **Bull**, Worden, Rogers, Cross, Dervilis [Investigating engineering data by probabilistic measures](https://link.springer.com/chapter/10.1007/978-3-030-12243-0_12) (2020)                                                                                                                                                                                                                     |
+| 61 | **Bull**, Worden, Rogers, Wickramarachchi, Cross, Mcleay, Leahy, Dervilis [A probabilistic framework for online structural health monitoring: active learning from machining data streams](https://iopscience.iop.org/article/10.1088/1742-6596/1264/1/012028/meta) (2019)                                                                                                                      |
+| 62 | **Bull**, Rogers, Dervilis, Cross, Worden [A Gaussian process form for population-based structural health monitoring](https://www.researchgate.net/profile/Lawrence-Bull-2/publication/334250549_A_Gaussian_process_form_for_population-based_structural_health_monitoring/links/622771023c53d31ba4b15c72/A-Gaussian-process-form-for-population-based-structural-health-monitoring.pdf) (2019) |
+| 63 | **Bull**, Dervilis, Worden [Experimental Validation of the Population-Form to Represent Nominally-Identical Systems](https://scholar.google.com/scholar?cluster=7507461710880003650&hl=en&oi=scholarr) (2019)                                                                                                                                                                                   |
+| 65 | **Bull**, Worden, Dervilis [Damage classification using labelled and unlabelled measurements](https://www.researchgate.net/profile/Lawrence-Bull-2/publication/337303717_Damage_Classification_Using_Labelled_and_Unlabelled_Measurements/links/62276fc93c53d31ba4b15c45/Damage-Classification-Using-Labelled-and-Unlabelled-Measurements.pdf) (2019)                                           |
+| 66 | Dervilis, Zhang, **Bull**, Cross, Rogers, Fuentes, Dertimanis, Abdallah, Chatzi, Worden [A nonlinear robust outlier detection approach for SHM](https://eprints.whiterose.ac.uk/147321/) (2019)                                                                                                                                                                                                 |
+| 67 | **Bull**, Manson, Worden, Dervilis [Active Learning Approaches to Structural Health Monitoring](https://link.springer.com/chapter/10.1007/978-3-319-75390-4_14) (2019)                                                                                                                                                                                                                          |
+| 69 | **Bull**, Worden, Cross, Dervilis [Outlier Ensembles: an Alternative Robust Method for Inclusive Outlier Analysis with Structural Health Monitoring Data](https://www.ndt.net/article/ewshm2018/papers/0093-Bill.pdf) (2018)                                                                                                                                                                    |
 

### 2024-04-24 writing.qmd
pubs update

--- 2023-01-15 writing.qmd
@@
 ## Notes
-### [Probability primer]()
-Notes for the ROSEHIPS reading group (TBC).
 
 ### [Introduction to Engineering Pattern Recognition](https://github.com/labull/EPR-lectures)
-Guest Lectures for the Advanced Dynamics course at the University of Sheffield in the Engineering dept.
+Initially guest Lectures for the Advanced Dynamics [MEC452] undergraduate course at the University of Sheffield in the Engineering Dept.
+
+Expanded to a workshop for the [IMAC conference, 2024](https://sem.org/pre-con-course-2).
+
 A light introduction to machine learning in the context of some engineering examples:

### 2024-08-28 index.qmd
UoG, LI and X links

@@
 
-Researcher in statistical methods for Data-Centric Engineering, specialising in monitoring techniques for telemetry data from systems and infrastructure.
+Researcher Fellow at [Glasgow University](https://www.gla.ac.uk/schools/mathematicsstatistics/staff/lawrencebull/#biography) in statistical methods for Data-Centric Engineering, specialising in monitoring techniques for telemetry data from systems and infrastructure.
 
@@
 
+[LinkedIn](https://www.linkedin.com/in/lawrence-bull-793178109/)
+
 [orcid](https://orcid.org/0000-0002-0225-5010)
 
-[twitter](https://twitter.com/lwrncebull?lang=ar)
+[X](https://x.com/lwrncebull)

### 2024-12-16 index.qmd
papers/bio update

@@
 
-Researcher Fellow at [Glasgow University](https://www.gla.ac.uk/schools/mathematicsstatistics/staff/lawrencebull/#biography) in statistical methods for Data-Centric Engineering, specialising in monitoring techniques for telemetry data from systems and infrastructure.
+Researcher Fellow [[Stats, UoG]](https://www.gla.ac.uk/schools/mathematicsstatistics/staff/lawrencebull/#biography) in machine learning for physical systems.
+Particularly tools to encode structure (via domain knowledge) into data-driven models.
+Statistical methods for telemetry data from machines and infrastructure.
 
-I'm interested in the dependencies that appear in measurements from populations of machines -- [planes](https://www.sciencedirect.com/science/article/pii/S0022460X21001449), [trains](https://arxiv.org/abs/2403.17820), [automobiles](https://doi.org/10.48550/arXiv.2204.12404) (...
+Applications have included [planes](https://www.sciencedirect.com/science/article/pii/S0022460X21001449), [trains](https://arxiv.org/abs/2403.17820), [automobiles](https://doi.org/10.48550/arXiv.2204.12404) (..
 [wind turbines](https://arxiv.org/abs/2111.15496)).
 By encoding domain expertise into statistical models, complex representations can be built from interpretable units, allowing machines to share information and increasing the value of data.
-<!-- At a systems level, alternative insights can emerge that might otherwise be missed -- the whole is something _besides_ its parts. -->
 

### 2024-12-16 papers.qmd
papers/bio update

--- 2023-05-26 papers.qmd
@@
 |---:|:------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------|
-|  3 | Poole, Gardner, Dervilis, **Bull**, Worden [On statistic alignment for domain adaptation in structural health monitoring](https://journals.sagepub.com/doi/abs/10.1177/14759217221110441) (2023)                                                                                          |
-|  5 | Hughes, **Bull**, Gardner, Dervilis, Worden [On robust risk-based active-learning algorithms for enhanced decision support](https://www.sciencedirect.com/science/article/pii/S0888327022006124) (2022)                                                                                   |
-|  6 | Dardeno, **Bull**, Mills, Dervilis, Worden [Modelling variability in vibration-based PBSHM via a generalised population form](https://www.sciencedirect.com/science/article/pii/S0022460X22004151) (2022)                                                                                 |
-|  7 | **Bull**, Dhada, Steinert, Lindgren, Parlikad, Duncan, Girolami [Knowledge Transfer in Engineering Fleets: Hierarchical Bayesian Modelling for Multi-Task Learning](https://arxiv.org/abs/2204.12404) (2022)                                                                              |
-|  8 | **Bull**, Dervilis, Worden, Cross, Rogers [A sampling-based approach for information-theoretic inspection management](https://royalsocietypublishing.org/doi/abs/10.1098/rspa.2021.0790) (2022)                                                                                           |
-| 14 | Gardner, **Bull**, Gosliga, Poole, Dervilis, Worden [A population-based SHM methodology for heterogeneous structures: Transferring damage localisation knowledge between different aircraft wings](https://www.sciencedirect.com/science/article/pii/S0888327022001030) (2022)            |
-| 15 | **Bull**, Gardner, Rogers, Dervilis, Cross, Papatheou, Maguire, Campos, Worden [Bayesian modelling of multivalued power curves from an operational wind farm](https://www.sciencedirect.com/science/article/pii/S0888327021008724) (2022)                                                 |
-| 16 | Gardner, **Bull**, Dervilis, Worden [Domain-adapted Gaussian mixture models for population-based structural health monitoring](https://link.springer.com/article/10.1007/s13349-022-00565-5) (2022)                                                                                       |
-| 18 | Gardner, **Bull**, Dervilis, Worden [On the application of kernelised Bayesian transfer learning to population-based structural health monitoring](https://www.sciencedirect.com/science/article/pii/S088832702100861X) (2022)                                                            |
-| 19 | Hughes, **Bull**, Gardner, Barthorpe, Dervilis, Worden [On risk-based active learning for structural health monitoring](https://www.sciencedirect.com/science/article/pii/S0888327021009055) (2022)                                                                                       |
-| 26 | Gardner, **Bull**, Dervilis, Worden [Overcoming the problem of repair in structural health monitoring: Metric-informed transfer learning](https://www.sciencedirect.com/science/article/pii/S0022460X21003175) (2021)                                                                     |
-| 28 | **Bull**, Gardner, Dervilis, Papatheou, Haywood-alexander, Mills, Worden [On the transfer of damage detectors between structures: An experimental case study](https://www.sciencedirect.com/science/article/pii/S0022460X21001449) (2021)                                                 |
-| 29 | **Bull**, Gardner, Rogers, Cross, Dervilis, Worden [Probabilistic inference for structural health monitoring: new modes of learning from data](https://ascelibrary.org/doi/abs/10.1061/AJRUA6.0001106) (2021)                                                                             |
-| 30 | Gardner, **Bull**, Gosliga, Dervilis, Worden [Foundations of population-based SHM, Part III: Heterogeneous populations–mapping and transfer](https://www.sciencedirect.com/science/article/pii/S0888327020305288) (2021)                                                                  |
-| 31 | **Bull**, Gardner, Gosliga, Rogers, Dervilis, Cross, Papatheou, Maguire, Campos, Worden [Foundations of population-based SHM, Part I: Homogeneous populations and forms](https://www.sciencedirect.com/science/article/pii/S0888327020305276) (2021)                                      |
-| 32 | Gosliga, Gardner, **Bull**, Dervilis, Worden [Foundations of Population-based SHM, Part II: Heterogeneous populations–Graphs, networks, and communities](https://www.sciencedirect.com/science/article/pii/S0888327020305306) (2021)                                                      |
-| 33 | Gardner, **Bull**, Gosliga, Poole, Dervilis, Worden [On a Population-Based Structural Health Monitoring Framework: An Aerospace Case Study](https://www.dpi-proceedings.com/index.php/shm2021/article/view/36243) (2021)                                                                  |
-| 34 | Dardeno, Haywood-alexander, Mills, **Bull**, Dervilis, Worden [Investigating the effects of ambient temperature on feature consistency in vibration-based SHM](https://www.dpi-proceedings.com/index.php/shm2021/article/view/36344) (2021)                                               |
-| 35 | Dardeno, **Bull**, Dervilis, Worden [Investigating experimental repeatability and feature consistency in vibration-based SHM](https://www.dpi-proceedings.com/index.php/shm2021/article/view/36346) (2021)                                                                                |
-| 36 | Poole, Gardner, Dervilis, **Bull**, Worden [On normalisation for domain adaptation in population-based structural health monitoring](https://www.dpi-proceedings.com/index.php/shm2021/article/view/36280) (2021)                                                                         |
-| 41 | Zammit, **Bull**, Sanders, Galvin, Dervilis, Sidhu, Worden [Towards the Probabilistic Analysis of Small Bowel Capsule Endoscopy Features to Predict Severity of Duodenal Histology in Patients with Villous Atrophy](https://link.springer.com/article/10.1007/s10916-020-01657-9) (2020) |
-| 42 | Worden, **Bull**, Gardner, Gosliga, Rogers, Cross, Papatheou, Lin, Dervilis [A brief introduction to recent developments in population-based structural health monitoring](https://www.frontiersin.org/articles/10.3389/fbuil.2020.00146/full) (2020)                                     |
-| 44 | **Bull**, Worden, Dervilis [Towards semi-supervised and probabilistic classification in structural health monitoring](https://www.sciencedirect.com/science/article/pii/S088832702030039X) (2020)                                                                                         |
-| 50 | **Bull**, Rogers, Wickramarachchi, Cross, Worden, Dervilis [Probabilistic active learning: an online framework for structural health monitoring](https://www.sciencedirect.com/science/article/pii/S0888327019305096) (2019)                                                              |
-| 51 | **Bull**, Worden, Fuentes, Manson, Cross, Dervilis [Outlier ensembles: A robust method for damage detection and unsupervised feature extraction from high-dimensional data](https://www.sciencedirect.com/science/article/pii/S0022460X1930197X) (2019)                                   |
-| 59 | **Bull**, Worden, Manson, Dervilis [Active learning for semi-supervised structural health monitoring](https://www.sciencedirect.com/science/article/pii/S0022460X18305479) (2018)                                                                                                         |
+|  8 | Dardeno, Worden, Dervilis, Mills, **Bull** [On the hierarchical Bayesian modelling of frequency response functions](https://www.sciencedirect.com/science/article/pii/S0888327023009809) (2024)                                                                                           |
+| 10 | Bee, Poole, Worden, Dervilis, **Bull** [Multitask feature selection within structural datasets](https://www.cambridge.org/core/journals/data-centric-engineering/article/multitask-feature-selection-within-structural-datasets/FC9171AF330232B4B07955F807C5BBD4) (2024)                  |
+| 20 | Poole, Gardner, Dervilis, **Bull**, Worden [On statistic alignment for domain adaptation in structural health monitoring](https://journals.sagepub.com/doi/abs/10.1177/14759217221110441) (2023)                                                                                          |
+| 21 | Gardner, **Bull**, Dervilis, Worden [Domain-adapted Gaussian mixture models for population-based structural health monitoring](https://link.springer.com/article/10.1007/s13349-022-00565-5) (2022)                                                                                       |
+| 22 | Hughes, **Bull**, Gardner, Dervilis, Worden [On robust risk-based active-learning algorithms for enhanced decision support](https://www.sciencedirect.com/science/article/pii/S0888327022006124) (2022)                                                                                   |
+| 23 | Dardeno, **Bull**, Mills, Dervilis, Worden [Modelling variability in vibration-based PBSHM via a generalised population form](https://www.sciencedirect.com/science/article/pii/S0022460X22004151) (2022)                                                                                 |
+| 24 | **Bull**, Dhada, Steinert, Lindgren, Parlikad, Duncan, Girolami [Knowledge Transfer in Engineering Fleets: Hierarchical Bayesian Modelling for Multi-Task Learning](https://scholar.google.com/scholar?cluster=9172883967640918731&hl=en&oi=scholarr) (2022)                              |
+| 25 | **Bull**, Dervilis, Worden, Cross, Rogers [A sampling-based approach for information-theoretic inspection management](https://royalsocietypublishing.org/doi/abs/10.1098/rspa.2021.0790) (2022)                                                                                           |
+| 31 | Gardner, **Bull**, Gosliga, Poole, Dervilis, Worden [A population-based SHM methodology for heterogeneous structures: Transferring damage localisation knowledge between different aircraft wings](https://www.sciencedirect.com/science/article/pii/S0888327022001030) (2022)            |
+| 32 | **Bull**, Gardner, Rogers, Dervilis, Cross, Papatheou, Maguire, Campos, Worden [Bayesian modelling of multivalued power curves from an operational wind farm](https://www.sciencedirect.com/science/article/pii/S0888327021008724) (2022)                                                 |
+| 34 | Gardner, **Bull**, Dervilis, Worden [On the application of kernelised Bayesian transfer learning to population-based structural health monitoring](https://www.sciencedirect.com/science/article/pii/S088832702100861X) (2022)                                                            |
+| 35 | Hughes, **Bull**, Gardner, Barthorpe, Dervilis, Worden [On risk-based active learning for structural health monitoring](https://www.sciencedirect.com/science/article/pii/S0888327021009055) (2022)                                                                                       |
+| 42 | Gardner, **Bull**, Dervilis, Worden [Overcoming the problem of repair in structural health monitoring: Metric-informed transfer learning](https://www.sciencedirect.com/science/article/pii/S0022460X21003175) (2021)                                                                     |
+| 44 | **Bull**, Gardner, Dervilis, Papatheou, Haywood-alexander, Mills, Worden [On the transfer of damage detectors between structures: An experimental case study](https://www.sciencedirect.com/science/article/pii/S0022460X21001449) (2021)                                                 |
+| 45 | **Bull**, Gardner, Rogers, Cross, Dervilis, Worden [Probabilistic inference for structural health monitoring: new modes of learning from data](https://ascelibrary.org/doi/abs/10.1061/AJRUA6.0001106) (2021)                                                                             |
+| 46 | Gardner, **Bull**, Gosliga, Dervilis, Worden [Foundations of population-based SHM, Part III: Heterogeneous populations–Mapping and transfer](https://www.sciencedirect.com/science/article/pii/S0888327020305288) (2021)                                                                  |
+| 47 | **Bull**, Gardner, Gosliga, Rogers, Dervilis, Cross, Papatheou, Maguire, Campos, Worden [Foundations of population-based SHM, Part I: Homogeneous populations and forms](https://www.sciencedirect.com/science/article/pii/S0888327020305276) (2021)                                      |
+| 48 | Gosliga, Gardner, **Bull**, Dervilis, Worden [Foundations of Population-based SHM, Part II: Heterogeneous populations–Graphs, networks, and communities](https://www.sciencedirect.com/science/article/pii/S0888327020305306) (2021)                                                      |
+| 49 | Gardner, **Bull**, Gosliga, Poole, Dervilis, Worden [On a Population-Based Structural Health Monitoring Framework: An Aerospace Case Study](https://www.dpi-proceedings.com/index.php/shm2021/article/view/36243) (2021)                                                                  |
+| 50 | Dardeno, Haywood-alexander, Mills, **Bull**, Dervilis, Worden [Investigating the effects of ambient temperature on feature consistency in vibration-based SHM](https://dpi-proceedings.com.destechpub.a2hosted.com/index.php/shm2021/article/view/36344) (2021)                           |
+| 51 | Dardeno, **Bull**, Dervilis, Worden [Investigating experimental repeatability and feature consistency in vibration-based SHM](https://www.dpi-proceedings.com/index.php/shm2021/article/view/36346) (2021)                                                                                |
+| 52 | Poole, Gardner, Dervilis, **Bull**, Worden [On normalisation for domain adaptation in population-based structural health monitoring](https://www.dpi-proceedings.com/index.php/shm2021/article/view/36280) (2021)                                                                         |
+| 57 | Zammit, **Bull**, Sanders, Galvin, Dervilis, Sidhu, Worden [Towards the Probabilistic Analysis of Small Bowel Capsule Endoscopy Features to Predict Severity of Duodenal Histology in Patients with Villous Atrophy](https://link.springer.com/article/10.1007/s10916-020-01657-9) (2020) |
+| 58 | Worden, **Bull**, Gardner, Gosliga, Rogers, Cross, Papatheou, Lin, Dervilis [A brief introduction to recent developments in population-based structural health monitoring](https://www.frontiersin.org/articles/10.3389/fbuil.2020.00146/full) (2020)                                     |
+| 60 | **Bull**, Worden, Dervilis [Towards semi-supervised and probabilistic classification in structural health monitoring](https://www.sciencedirect.com/science/article/pii/S088832702030039X) (2020)                                                                                         |
+| 66 | **Bull**, Rogers, Wickramarachchi, Cross, Worden, Dervilis [Probabilistic active learning: an online framework for structural health monitoring](https://www.sciencedirect.com/science/article/pii/S0888327019305096) (2019)                                                              |
+| 67 | **Bull**, Worden, Fuentes, Manson, Cross, Dervilis [Outlier ensembles: A robust method for damage detection and unsupervised feature extraction from high-dimensional data](https://www.sciencedirect.com/science/article/pii/S0022460X1930197X) (2019)                                   |
+| 75 | **Bull**, Worden, Manson, Dervilis [Active learning for semi-supervised structural health monitoring](https://www.sciencedirect.com/science/article/pii/S0022460X18305479) (2018)                                                                                                         |
 
 |    | Preprints                                                                                                                                                                                                        |
-|---:|:-------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------|
-|  1 | Bee, **Bull**, Dervilis, Worden [When is an SHM problem a Multi-Task-Learning problem?](https://arxiv.org/abs/2305.09425) (2023)                                                                                   |
-|  2 | **Bull**, Jones, Cross, Duncan, Girolami [Encoding Domain Expertise into Multilevel Models for Source Location](https://arxiv.org/abs/2305.08657) (2023)                                                           |
-|  4 | Bee, Papatheou, Haywood-alexander, Mills, **Bull**, Worden, Dervilis [Better Together: Using Multi-task Learning to Improve Feature Selection within Structural Datasets](https://arxiv.org/abs/2303.04486) (2023) |
-|  9 | Hughes, **Bull**, Gardner, Dervilis, Worden [Mitigating sampling bias in risk-based active learning via an EM algorithm](https://arxiv.org/abs/2206.12598) (2022)                                                  |
-| 10 | Dardeno, **Bull**, Dervilis, Worden [A generalised form for a homogeneous population of structures using an overlapping mixture of Gaussian processes](https://arxiv.org/abs/2206.11683) (2022)                    |
-| 11 | Hughes, Gardner, **Bull**, Dervilis, Worden [Improving decision-making via risk-based active learning: Probabilistic discriminative classifiers](https://arxiv.org/abs/2206.11616) (2022)                          |
+|---:|:-----------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------|
+|  1 | Dardeno, **Bull**, Dervilis, Worden [When does a bridge become an aeroplane?](https://arxiv.org/abs/2411.18406) (2024)                                                                                           |
+|  2 | Clarkson, **Bull**, Wickramarachchi, Cross, Rogers, Worden, Dervilis, Hughes [Active learning for regression in engineering populations: A risk-informed approach](https://arxiv.org/abs/2409.04328) (2024)      |
+|  3 | Brealy, Hughes, Dardeno, **Bull**, Mills, Dervilis, Worden [Multitask learning for improved scour detection: A dynamic wave tank study](https://arxiv.org/abs/2408.16527) (2024)                                 |
+|  6 | **Bull**, Jeon, Girolami, Duncan, Schooling, Haro [Towards Multilevel Modelling of Train Passing Events on the Staffordshire Bridge](https://arxiv.org/abs/2403.17820) (2024)                                    |
+|  7 | Smith, Hughes, Dardeno, **Bull**, Dervilis, Worden [Anomaly Detection in Offshore Wind Turbine Structures using Hierarchical Bayesian Modelling](https://arxiv.org/abs/2402.19295) (2024)                        |
+| 12 | Clarkson, **Bull**, Dardeno, Wickramarachchi, Cross, Rogers, Worden, Dervilis, Hughes [Sharing Information Between Machine Tools to Improve Surface Finish Forecasting](https://arxiv.org/abs/2310.05807) (2023) |
+| 18 | Bee, **Bull**, Dervilis, Worden [When is an SHM problem a Multi-Task-Learning problem?](https://arxiv.org/abs/2305.09425) (2023)                                                                                 |
+| 19 | **Bull**, Jones, Cross, Duncan, Girolami [Encoding domain expertise into multilevel models for source location](https://arxiv.org/abs/2305.08657) (2023)                                                         |
+| 26 | Hughes, **Bull**, Gardner, Dervilis, Worden [Mitigating sampling bias in risk-based active learning via an EM algorithm](https://arxiv.org/abs/2206.12598) (2022)                                                |
+| 27 | Dardeno, **Bull**, Dervilis, Worden [A generalised form for a homogeneous population of structures using an overlapping mixture of Gaussian processes](https://arxiv.org/abs/2206.11683) (2022)                  |
+| 28 | Hughes, Gardner, **Bull**, Dervilis, Worden [Improving decision-making via risk-based active learning: Probabilistic discriminative classifiers](https://arxiv.org/abs/2206.11616) (2022)                        |
 
 |    | Book chapters                                                                                                                                                                                                                                                                                                                                       |
-|---:|:------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------|
-| 21 | **Bull**, Hughes, Rogers, Gardner, Worden, Dervilis [Partially Supervised Learning for Data-Driven Structural Health Monitoring](https://link.springer.com/chapter/10.1007/978-3-030-81716-9_19) (2022)                       |
-| 22 | Gardner, **Bull**, Gosliga, Dervilis, Cross, Papatheou, Worden [Population-Based Structural Health Monitoring](https://link.springer.com/chapter/10.1007/978-3-030-81716-9_20) (2022)                                         |
-| 45 | Fuentes, Cross, Gardner, **Bull**, Rogers, Barthorpe, Shi, Dervilis, Farrar, Worden [Structural Health Monitoring and Damage Identification](https://link.springer.com/content/pdf/10.1007/978-1-4939-6503-8_23-1.pdf) (2020) |
+|---:|:----------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------|
+| 11 | **Bull**, Abdallah, Mylonas, Avendaño-valencia, Tatsis, Gardner, Rogers, Brennan, Cross, Worden, Duncan, Dervilis, Girolami, Chatzi [Data-Centric Monitoring of Wind Farms](https://books.google.com/books?hl=en&lr=&id=x57WEAAAQBAJ&oi=fnd&pg=PA206&dq=info:opW30yPHEQIJ:scholar.google.com&ots=4hJqDfiRLw&sig=zoF7f3rVwlT5m2QngGMDM4H49Yw) (2023) |
+| 37 | **Bull**, Hughes, Rogers, Gardner, Worden, Dervilis [Partially Supervised Learning for Data-Driven Structural Health Monitoring](https://link.springer.com/chapter/10.1007/978-3-030-81716-9_19) (2022)                                                                                                                                             |
+| 38 | Gardner, **Bull**, Gosliga, Dervilis, Cross, Papatheou, Worden [Population-Based Structural Health Monitoring](https://link.springer.com/chapter/10.1007/978-3-030-81716-9_20) (2022)                                                                                                                                                               |
+| 61 | Fuentes, Cross, Gardner, **Bull**, Rogers, Barthorpe, Shi, Dervilis, Farrar, Worden [Structural Health Monitoring and Damage Identification](https://link.springer.com/content/pdf/10.1007/978-1-4939-6503-8_23-1.pdf) (2020)                                                                                                                       |
 
@@
 |---:|:--------------------------------------------------------------------------------------------------------------------------------------|
-| 55 | **Bull** [Towards probabilistic and partially-supervised structural health monitoring](https://etheses.whiterose.ac.uk/26282/) (2019) |
+| 71 | **Bull** [Towards probabilistic and partially-supervised structural health monitoring](https://etheses.whiterose.ac.uk/26282/) (2019) |
 
@@
 |---:|:------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------|
-| 12 | Poole, Gardner, Dervilis, **Bull**, Worden [On the Application of Partial Domain Adaptation for PBSHM](https://link.springer.com/chapter/10.1007/978-3-031-07322-9_42) (2022)                                                                                                                                                                                                                   |
-| 13 | Dhada, **Bull**, Girolami, Parlikad [Modelling the Times-to-Failures Using a Statistical Hierarchical Model](https://link.springer.com/chapter/10.1007/978-3-031-07258-1_99) (2022)                                                                                                                                                                                                             |
-| 17 | **Bull**, Dhada, Steinert, Lindgren, Parlikad, Girolami [Population-Level Modelling for Truck Fleet Survival Analysis](https://www.repository.cam.ac.uk/bitstreams/905dbe0a-1a73-4fc5-861f-9ff7a9c816c9/download) (2022)                                                                                                                                                                        |
-| 20 | Hughes, **Bull**, Gardner, Dervilis, Worden, Hughes [Semi-supervised risk-based active learning using inspection and maintenance information](https://eprints.whiterose.ac.uk/191598/) (2022)                                                                                                                                                                                                   |
-| 23 | Gardner, **Bull**, Dervilis, Worden [Challenges for SHM from Structural Repairs: An Outlier-Informed Domain Adaptation Approach](https://link.springer.com/chapter/10.1007/978-3-030-76004-5_10) (2022)                                                                                                                                                                                         |
-| 24 | Gardner, **Bull**, Dervilis, Worden [On the Application of Heterogeneous Transfer Learning to Population-Based Structural Health Monitoring](https://link.springer.com/chapter/10.1007/978-3-030-76004-5_11) (2022)                                                                                                                                                                             |
-| 25 | **Bull**, Gardner, Dervilis, Papatheou, Haywood-alexander, Mills, Worden [Transferring Damage Detectors Between Tailplane Experiments](https://link.springer.com/chapter/10.1007/978-3-030-76004-5_22) (2022)                                                                                                                                                                                   |
-| 27 | Hughes, **Bull**, Gardner, Barthorpe, Dervilis, Worden [A risk-based active learning approach to inspection scheduling](https://www.researchgate.net/profile/Aidan-Hughes-4/publication/355903488_A_risk-based_active_learning_approach_to_inspection_scheduling/links/61892373d7d1af224bc69a96/A-risk-based-active-learning-approach-to-inspection-scheduling.pdf) (2021)                      |
-| 37 | **Bull**, Gardner, Dervilis, Papatheou, Worden [Automated Feature Extraction for Damage Detection: A Pseudo-fault Framework for Population-based SHM]() (2021)                                                                                                                                                                                                                                  |
-| 38 | **Bull**, Gardner, Dervilis, Worden [Normalising Flows and Nonlinear Normal Modes](https://www.sciencedirect.com/science/article/pii/S240589632101209X) (2021)                                                                                                                                                                                                                                  |
-| 39 | Gosliga, Gardner, **Bull**, Dervilis, Worden [Towards population-based structural health monitoring, Part III: Graphs, networks and communities](https://link.springer.com/chapter/10.1007/978-3-030-47717-2_26) (2021)                                                                                                                                                                         |
-| 40 | Gosliga, Gardner, **Bull**, Dervilis, Worden [Towards population-based structural health monitoring, Part II: heterogeneous populations and structures as graphs](https://link.springer.com/chapter/10.1007/978-3-030-47717-2_17) (2021)                                                                                                                                                        |
-| 43 | **Bull**, Gardner, Rogers, Cross, Dervilis, Worden [New Modes of Inference for Probabilistic SHM](https://link.springer.com/chapter/10.1007/978-3-030-64908-1_39) (2020)                                                                                                                                                                                                                        |
-| 46 | Gardner, **Bull**, Gosliga, Dervilis, Worden [Towards population-based structural health monitoring, Part IV: heterogeneous populations, transfer and mapping](https://link.springer.com/chapter/10.1007/978-3-030-47638-0_20) (2020)                                                                                                                                                           |
-| 47 | Gardner, **Bull**, Dervilis, Worden [Kernelised Bayesian transfer learning for population-based structural health monitoring](https://link.springer.com/chapter/10.1007/978-3-030-47638-0_22) (2020)                                                                                                                                                                                            |
-| 48 | **Bull**, Gardner, Gosliga, Dervilis, Papatheou, Maguire, Campos, Rogers, Cross, Worden [Towards population-based structural health monitoring, Part I: Homogeneous populations and forms](https://link.springer.com/chapter/10.1007/978-3-030-47638-0_32) (2020)                                                                                                                               |
-| 49 | **Bull**, Worden, Rogers, Cross, Dervilis [Investigating engineering data by probabilistic measures](https://link.springer.com/chapter/10.1007/978-3-030-12243-0_12) (2020)                                                                                                                                                                                                                     |
-| 52 | **Bull**, Worden, Rogers, Wickramarachchi, Cross, Mcleay, Leahy, Dervilis [A probabilistic framework for online structural health monitoring: active learning from machining data streams](https://iopscience.iop.org/article/10.1088/1742-6596/1264/1/012028/meta) (2019)                                                                                                                      |
-| 53 | **Bull**, Rogers, Dervilis, Cross, Worden [A Gaussian process form for population-based structural health monitoring](https://www.researchgate.net/profile/Lawrence-Bull-2/publication/334250549_A_Gaussian_process_form_for_population-based_structural_health_monitoring/links/622771023c53d31ba4b15c72/A-Gaussian-process-form-for-population-based-structural-health-monitoring.pdf) (2019) |
-| 54 | **Bull**, Dervilis, Worden [Experimental Validation of the Population-Form to Represent Nominally-Identical Systems](https://www.dpi-proceedings.com/index.php/shm2019/article/view/32373) (2019)                                                                                                                                                                                               |
-| 56 | **Bull**, Worden, Dervilis [Damage classification using labelled and unlabelled measurements](https://www.researchgate.net/profile/Lawrence-Bull-2/publication/337303717_Damage_Classification_Using_Labelled_and_Unlabelled_Measurements/links/62276fc93c53d31ba4b15c45/Damage-Classification-Using-Labelled-and-Unlabelled-Measurements.pdf) (2019)                                           |
-| 57 | Dervilis, Zhang, **Bull**, Cross, Rogers, Fuentes, Dertimanis, Abdallah, Chatzi, Worden [A nonlinear robust outlier detection approach for SHM](https://eprints.whiterose.ac.uk/147321/) (2019)                                                                                                                                                                                                 |
-| 58 | **Bull**, Manson, Worden, Dervilis [Active Learning Approaches to Structural Health Monitoring](https://link.springer.com/chapter/10.1007/978-3-319-75390-4_14) (2019)                                                                                                                                                                                                                          |
-| 60 | **Bull**, Worden, Cross, Dervilis [Outlier Ensembles: an Alternative Robust Method for Inclusive Outlier Analysis with Structural Health Monitoring Data]() (2018)                                                                                                                                                                                                                              |
+|  4 | Brealy, **Bull**, Brennan, Beltrando, Sommer, Dervilis, Worden [On Additive Gaussian Processes for Wind Farm Power Prediction](https://link.springer.com/chapter/10.1007/978-3-031-61425-5_58) (2024)                                                                                                                                                                                           |
+|  5 | Dardeno, **Bull**, Dervilis, Worden [Transfer learning via intermediate structures](https://eprints.whiterose.ac.uk/212847/) (2024)                                                                                                                                                                                                                                                             |
+|  9 | Dardeno, **Bull**, Dervilis, Worden [Decoupling nonlinear normal modes using normalising flows](https://eprints.whiterose.ac.uk/212848/) (2024)                                                                                                                                                                                                                                                 |
+| 13 | Dardeno, **Bull**, Mills, Dervilis, Worden [Hierarchical Bayesian modelling of a family of FRFs](https://eprints.whiterose.ac.uk/212849/) (2023)                                                                                                                                                                                                                                                |
+| 14 | Dardeno, **Bull**, Mills, Dervilis, Worden [Hierarchical Bayes for population-based modelling of FRFs with temperature variation](https://eprints.whiterose.ac.uk/212850/) (2023)                                                                                                                                                                                                               |
+| 15 | Dardeno, **Bull**, Dervilis, Worden [A population form via hierarchical Bayesian modelling of the FRF](https://link.springer.com/chapter/10.1007/978-3-031-34946-1_11) (2023)                                                                                                                                                                                                                   |
+| 16 | Haywood-alexander, Worden, Dervilis, Mills, **Bull**, Dardeno [The Astir Glider Wing Dataset for Population-Based SHM](https://link.springer.com/chapter/10.1007/978-3-031-37007-6_3) (2023)                                                                                                                                                                                                    |
+| 17 | Bee, Papatheou, Haywood-alexander, Mills, **Bull**, Worden, Dervilis [Better Together: Using Multi-Task Learning to Improve Feature Selection Within Structural Datasets](https://link.springer.com/chapter/10.1007/978-3-031-34946-1_7) (2023)                                                                                                                                                 |
+| 29 | Poole, Gardner, Dervilis, **Bull**, Worden [On the application of partial domain adaptation for pbshm](https://link.springer.com/chapter/10.1007/978-3-031-07322-9_42) (2022)                                                                                                                                                                                                                   |
+| 30 | Dhada, **Bull**, Girolami, Parlikad [Modelling the Times-to-Failures Using a Statistical Hierarchical Model](https://link.springer.com/chapter/10.1007/978-3-031-07258-1_99) (2022)                                                                                                                                                                                                             |
+| 33 | **Bull**, Dhada, Steinert, Lindgren, Parlikad, Girolami [Population-Level Modelling for Truck Fleet Survival Analysis](https://www.repository.cam.ac.uk/items/f7d7fc3d-a2bd-412d-b7da-e5c5e40c1392) (2022)                                                                                                                                                                                      |
+| 36 | Hughes, **Bull**, Gardner, Dervilis, Worden, Hughes [Semi-supervised risk-based active learning using inspection and maintenance information](https://eprints.whiterose.ac.uk/191598/) (2022)                                                                                                                                                                                                   |
+| 39 | Gardner, **Bull**, Dervilis, Worden [Challenges for SHM from Structural Repairs: An Outlier-Informed Domain Adaptation Approach](https://link.springer.com/chapter/10.1007/978-3-030-76004-5_10) (2022)                                                                                                                                                                                         |
+| 40 | Gardner, **Bull**, Dervilis, Worden [On the Application of Heterogeneous Transfer Learning to Population-Based Structural Health Monitoring](https://link.springer.com/chapter/10.1007/978-3-030-76004-5_11) (2022)                                                                                                                                                                             |
+| 41 | **Bull**, Gardner, Dervilis, Papatheou, Haywood-alexander, Mills, Worden [Transferring Damage Detectors Between Tailplane Experiments](https://link.springer.com/chapter/10.1007/978-3-030-76004-5_22) (2022)                                                                                                                                                                                   |
+| 43 | Hughes, **Bull**, Gardner, Barthorpe, Dervilis, Worden [A risk-based active learning approach to inspection scheduling](https://www.researchgate.net/profile/Aidan-Hughes-4/publication/355903488_A_risk-based_active_learning_approach_to_inspection_scheduling/links/61892373d7d1af224bc69a96/A-risk-based-active-learning-approach-to-inspection-scheduling.pdf) (2021)                      |
+| 53 | **Bull**, Gardner, Dervilis, Papatheou, Worden [Automated Feature Extraction for Damage Detection: A Pseudo-fault Framework for Population-based SHM]() (2021)                                                                                                                                                                                                                                  |
+| 54 | **Bull**, Gardner, Dervilis, Worden [Normalising Flows and Nonlinear Normal Modes](https://www.sciencedirect.com/science/article/pii/S240589632101209X) (2021)                                                                                                                                                                                                                                  |
+| 55 | Gosliga, Gardner, **Bull**, Dervilis, Worden [Towards population-based structural health monitoring, Part III: Graphs, networks and communities](https://link.springer.com/chapter/10.1007/978-3-030-47717-2_26) (2021)                                                                                                                                                                         |
+| 56 | Gosliga, Gardner, **Bull**, Dervilis, Worden [Towards population-based structural health monitoring, Part II: heterogeneous populations and structures as graphs](https://link.springer.com/chapter/10.1007/978-3-030-47717-2_17) (2021)                                                                                                                                                        |
+| 59 | **Bull**, Gardner, Rogers, Cross, Dervilis, Worden [New Modes of Inference for Probabilistic SHM](https://link.springer.com/chapter/10.1007/978-3-030-64908-1_39) (2020)                                                                                                                                                                                                                        |
+| 62 | Gardner, **Bull**, Gosliga, Dervilis, Worden [Towards population-based structural health monitoring, Part IV: heterogeneous populations, transfer and mapping](https://link.springer.com/chapter/10.1007/978-3-030-47638-0_20) (2020)                                                                                                                                                           |
+| 63 | Gardner, **Bull**, Dervilis, Worden [Kernelised Bayesian transfer learning for population-based structural health monitoring](https://link.springer.com/chapter/10.1007/978-3-030-47638-0_22) (2020)                                                                                                                                                                                            |
+| 64 | **Bull**, Gardner, Gosliga, Dervilis, Papatheou, Maguire, Campos, Rogers, Cross, Worden [Towards population-based structural health monitoring, Part I: Homogeneous populations and forms](https://link.springer.com/chapter/10.1007/978-3-030-47638-0_32) (2020)                                                                                                                               |
+| 65 | **Bull**, Worden, Rogers, Cross, Dervilis [Investigating engineering data by probabilistic measures](https://link.springer.com/chapter/10.1007/978-3-030-12243-0_12) (2020)                                                                                                                                                                                                                     |
+| 68 | **Bull**, Worden, Rogers, Wickramarachchi, Cross, Mcleay, Leahy, Dervilis [A probabilistic framework for online structural health monitoring: active learning from machining data streams](https://iopscience.iop.org/article/10.1088/1742-6596/1264/1/012028/meta) (2019)                                                                                                                      |
+| 69 | **Bull**, Rogers, Dervilis, Cross, Worden [A Gaussian process form for population-based structural health monitoring](https://www.researchgate.net/profile/Lawrence-Bull-2/publication/334250549_A_Gaussian_process_form_for_population-based_structural_health_monitoring/links/622771023c53d31ba4b15c72/A-Gaussian-process-form-for-population-based-structural-health-monitoring.pdf) (2019) |
+| 70 | **Bull**, Dervilis, Worden [Experimental Validation of the Population-Form to Represent Nominally-Identical Systems](https://www.dpi-proceedings.com/index.php/shm2019/article/view/32373) (2019)                                                                                                                                                                                               |
+| 72 | **Bull**, Worden, Dervilis [Damage classification using labelled and unlabelled measurements](https://www.researchgate.net/profile/Lawrence-Bull-2/publication/337303717_Damage_Classification_Using_Labelled_and_Unlabelled_Measurements/links/62276fc93c53d31ba4b15c45/Damage-Classification-Using-Labelled-and-Unlabelled-Measurements.pdf) (2019)                                           |
+| 73 | Dervilis, Zhang, **Bull**, Cross, Rogers, Fuentes, Dertimanis, Abdallah, Chatzi, Worden [A nonlinear robust outlier detection approach for SHM](https://eprints.whiterose.ac.uk/147321/) (2019)                                                                                                                                                                                                 |
+| 74 | **Bull**, Manson, Worden, Dervilis [Active Learning Approaches to Structural Health Monitoring](https://link.springer.com/chapter/10.1007/978-3-319-75390-4_14) (2019)                                                                                                                                                                                                                          |
+| 76 | **Bull**, Worden, Cross, Dervilis [Outlier Ensembles: an Alternative Robust Method for Inclusive Outlier Analysis with Structural Health Monitoring Data](https://scholar.google.com/scholar?cluster=10239515907274643620&hl=en&oi=scholarr) (2018)                                                                                                                                             |
+| 77 | Clarkson, **Bull**, Dardeno, Wickramarachchi, Cross, Rogers, Worden, Dervilis, Hughes [A spin on active learning analysis for health monitoring](https://www.ndt.net/article/ewshm2024/papers/242_manuscript.pdf) (None)                                                                                                                                                                        |
 

### 2024-12-17 index.qmd
bio update

@@
 
-Researcher Fellow [[Stats, UoG]](https://www.gla.ac.uk/schools/mathematicsstatistics/staff/lawrencebull/#biography) in machine learning for physical systems.
+Research Fellow [[Stats, UoG]](https://www.gla.ac.uk/schools/mathematicsstatistics/staff/lawrencebull/#biography) in machine learning for physical systems.
 Particularly tools to encode structure (via domain knowledge) into data-driven models.

### 2024-12-17 index.qmd
bio update

@@
 
-Research Fellow [[Stats, UoG]](https://www.gla.ac.uk/schools/mathematicsstatistics/staff/lawrencebull/#biography) in machine learning for physical systems.
+Research Fellow in machine learning for physical systems.
 Particularly tools to encode structure (via domain knowledge) into data-driven models.
-Statistical methods for telemetry data from machines and infrastructure.
+Mostly to monitor and simulate machines/infrastructure, by utilising telemetry data.
 
@@
 [wind turbines](https://arxiv.org/abs/2111.15496)).
-By encoding domain expertise into statistical models, complex representations can be built from interpretable units, allowing machines to share information and increasing the value of data.
+By encoding domain expertise into statistical models, complex representations can be built from interpretable units, increasing the value of sensing and fusing physics with data.
 
